### 2018-11-18 GroupfouR_TermProject.Rmd
Create GroupfouR_TermProject.Rmd

---
title: "GroupfouRTermProject"
output: html_document
---

Firstly, load the required packages

```{r, warning=FALSE}

library(tidyverse)
library(tidyverse)
library(readxl)
library(dplyr)

```

We exported 40 files from TradeMap.org website consisting of import and export statistics of Turkey in terms of total value and quantity per product group against the G7 countries (Germany, USA, UK, France, Italy, Japan and Canada) + 3 big economies namely Russia, India and India.

In order analyse, we should merge this files to create two data tables - one for import dataset and one for export dataset.

Firstly, we are merging the Turkey's import data by quantity against all 10 selected countries :

```{r}
PATH <-"C:/Users/avs1400/Desktop/master/DataAnEssR_503/odev"

rm(Quantdataset)
rm(Valuedataset)
rm(jTable)

nm <- list.files(path = PATH, pattern = '*.mport.*uant.*')
for (file in nm){

  # if the merged dataset doesn't exist, create it
  if (!exists("Quantdataset")){
    Quantdataset <- read_excel(file, col_names=FALSE, skip=1)
  }
  else{
    temp_dataset <-read_excel(file, col_names=FALSE, skip=1)
    Quantdataset<-rbind(Quantdataset, temp_dataset)
    rm(temp_dataset)
  }

}

```

After merging, naming the columns:

```{r}

colnames(Quantdataset) <- c("Country","Product_Code","Product_Label","2013_Quantity","Unit1","2014_Quantity","Unit2","2015_Quantity","Unit3","2016_Quantity","Unit4","2017_Quantity","Unit5")

```

Then, merging the the Turkey's import data by value against all 10 selected countries :

```{r}
nm <- list.files(path = PATH, pattern = '*.mport.*alu.*')
#rm(Valuedataset)

for (file in nm){

  # if the merged dataset doesn't exist, create it
  if (!exists("Valuedataset")){
    Valuedataset <- read_excel(file, col_names=FALSE, skip=1)
  }
  else{
    temp_dataset <-read_excel(file, col_names=FALSE, skip=1)
    Valuedataset<-rbind(Valuedataset, temp_dataset)
    rm(temp_dataset)
  }

}
```

And, naming the columns:

```{r}
colnames(Valuedataset) <- c("Country","Product_Code","Product_Label","2013_Value","2014_Value","2015_Value","2016_Value","2017_Value")
```

Now, we can full-join Turkey's import data by quantity and value:

```{r}

jTable <- Quantdataset %>% 
  mutate( Unit= coalesce(Unit1,Unit2 ,Unit3 , Unit4,Unit5)) %>%
  select( Country, Product_Code , Unit, "2013_Quantity", "2014_Quantity","2015_Quantity","2016_Quantity","2017_Quantity") %>% 
  full_join(Valuedataset,by = c("Country","Product_Code"))

```

### 2018-11-18 sourceCode/proje.R
Add files via upload

@@ -1,0 +1,67 @@
+library(tidyverse)
+library(readxl)
+library(dplyr)
+
+PATH <-"C:/Users/Desktop/master/DataAnEssR_503/odev"
+setwd(PATH)
+
+
+getDataSet <- function(pPattern){
+  nm <- list.files(path = PATH, pattern = pPattern)  
+  if (exists("resultDataset")){
+    rm("resultDataset")
+  }
+  for (file in nm){
+    if (!exists("resultDataset")){
+      resultDataset <- read_excel(file, col_names=FALSE, skip=1)
+    }
+    else{
+      temp_dataset <-read_excel(file, col_names=FALSE, skip=1)
+      resultDataset<-rbind(resultDataset, temp_dataset)
+      rm(temp_dataset)
+    }
+    
+  }
+  return(resultDataset)
+  
+}
+
+if (exists("import_quantity_dataset")){
+  rm("import_quantity_dataset")    
+}  
+if (exists("import_value_dataset")){
+  rm("import_value_dataset")    
+}  
+if (exists("import_jTable")){
+  rm("import_jTable")
+}
+if (exists("export_quantity_dataset")){
+  rm("export_quantity_dataset")    
+}  
+if (exists("export_value_dataset")){
+  rm("export_value_dataset")    
+}  
+if (exists("export_jTable")){
+  rm("export_jTable")
+}
+
+import_quantity_dataset <- getDataSet('*.mport.*uant.*')
+import_value_dataset <- getDataSet('*.mport.*alu.*')
+export_quantity_dataset <- getDataSet('*.xport.*uant.*')
+export_value_dataset <- getDataSet('*.xport.*alu.*')
+
+colnames(import_quantity_dataset) <- c("Country","Product_Code","Product_Label","Quantity_2013","Unit1","Quantity_2014","Unit2","Quantity_2015","Unit3","Quantity_2016","Unit4","Quantity_2017","Unit5")
+colnames(import_value_dataset) <- c("Country","Product_Code","Product_Label","Value_2013","Value_2014","Value_2015","Value_2016","Value_2017")
+colnames(export_quantity_dataset) <- c("Country","Product_Code","Product_Label","Quantity_2013","Unit1","Quantity_2014","Unit2","Quantity_2015","Unit3","Quantity_2016","Unit4","Quantity_2017","Unit5")
[…]

### 2018-12-13 sourceCode/projeEMRE.R
Update projeEMRE.R

@@ -215,4 +215,5 @@ plotRusIm <- ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 
 
 library(gridExtra)
 
-grid.arrange(plotCanEx, plotCanIm, plotRusEx, plotRusIm,  nrow = 2)
+grid.arrange(plotCanEx, plotCanIm,  nrow = 2)
+grid.arrange(plotRusEx, plotRusIm,  nrow = 2)

### 2018-12-13 Proposal.Rmd
.

---
title: "Group Fou*R* Term Project Proposal"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
output: html_document
---

We will export trade data of Turkey from trademap.org website which provides trade statistics for international business development.

Our aim is to analyze Turkey’s trade characteristics by product groups against 10 selected countries (G7 countries and Russia, India, China) and to summarize the Turkey’s overall trade statistics in this frame.

We will start with exporting total annual value of export and import of Turkey and quantities by product group against the target selected countries in the website. These data will include 5 years period from 2013 to 2017. Secondly, since the exported data are consist of 40 excel files (10 countries(trade against 10 countries) * 2 trade type (export and import) * 2 metric (trade value and trade quantity)), we will combine these files. Then, we will clean the data if needed and finally, we will analyze the data.

Through the analysis and visualization of the data, our object is to use explanatory analysis and visualization skills with data manipulation functions of like dplyr, reshape etc and visualition tools like ggplot, shiny and any other packages we will explore.

### 2018-12-13 Proposal.Rmd
.

@@
 ---
-title: "Group Fou*R* Term Project Proposal"
+title: "Group Fou\\*R* Term Project Proposal"
 subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"

### 2018-12-13 PreliminaryAnalysis.Rmd
.

---
title: "Group Fou\\*R* Term Project - Summary of Raw Data, Explanations and Preliminary Analysis"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
date: "December 2018"
output: html_document
---
## Explanatory Data Analysis of Trade Statistics of Turkey

### Abstract

We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey’s trade characteristics by product groups. Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017. 
In this study, We applied data manipulation to make it proper for analysis and explanatory data analysis with visulations and conclude with overall statistical overview of Turkey's trade.

### Explanation of Raw Data

Following the extraction from source (Trademap.org), our raw data consist of 10 countries’ trade data against Turkey. This data splits to 2 with trade direction as “Export” and “Import”. The other dimension is stat for trade, one is “Quantity” of Export/Import, the other is “Value” in billion USD of Export/Import. Therefore we have four main data frame for each country (total of 40 excel files).

<table>
<thead>
<tr class="header">
<th align="left">Data Frame</th>
<th align="left">DF Definition</th>
</tr>
</thead>

<tbody>
<tr class="odd">
<td align="left">ExportValues</td>
<td align="left">Export from Turkey to target countries and their values in billion USD</td>
</tr>
<tr class="odd">
<td align="left">ExportQuantity</td>
<td align="left">Export from Turkey to target countries and their quantities in units(tons,gallons etc)</td>
</tr>
<tr class="odd">
<td align="left">ImportValues</td>
<td align="left">Import to Turkey from target counties and their values in billion USD</td>
</tr>
<tr class="odd">
<td align="left">ImportQuantity</td>
<td align="left">Import to Turkey from target counties and their quantities in units(tons,gallons etc)</td>
</tr>

</tbody>
</table>

Table structures for "Quantity" and "Value" files are as follows:

<table>
<thead>
<tr class="header">
<th align="left">Country</th>
<th align="left">Product code</th>
<th align="left">Product label</th>
<th align="left">Quantity in 2013</th>
<th align="left">Unit</th>
<th align="left">Quantity in 2014</th>
<th align="left">Unit</th>
<th align="left">Quantity in 2015</th>
<th align="left">Unit</th>
<th align="left">Quantity in 2016</th>
<th align="left">Unit</th>
<th align="left">Quantity in 2017</th>
<th align="left">Unit</th>
</tr>
</thead>

<tbody>
<tr class="odd">
<td align="left">France</td>
<td align="left">'0306</td>
<td align="left">Crustaceans, whether in shell or not, live, fresh, chilled, frozen, dried, salted or in brine, ...</td>
<td align="left">121</td>
<td align="left">Tons</td>
<td align="left">139</td>
<td align="left">Tons</td>
<td align="left">22</td>
<td align="left">Tons</td>
<td align="left">24</td>
<td align="left">Tons</td>

</tr>
</tbody>
</table>

Table 1: Quantity excel table structure

<table>
<thead>
<tr class="header">
<th align="left">Country</th>
<th align="left">Product code</th>
<th align="left">Product label</th>
<th align="left">Value in 2013</th>
<th align="left">Value in 2014</th>
<th align="left">Value in 2015</th>
<th align="left">Value in 2016</th>
<th align="left">Value in 2017</th>
</tr>
</thead>

<tbody>
<tr class="odd">
<td align="left">France</td>
<td align="left">'0306</td>
<td align="left">Crustaceans, whether in shell or not, live, fresh, chilled, frozen, dried, salted or in brine, ...</td>
<td align="left">0</td>
<td align="left">1155</td>
<td align="left">1182</td>
<td align="left">270</td>
<td align="left">0</td>
</tr>
</tbody>
</table>

Table 2: Values excel table structure

In addition to main raw data, we also have look-up table for product codes; This lookup table registers product labels in 2 digit code that is less categorized than main data.

<table>
<thead>
<tr class="header">
<th align="left">Product code</th>
<th align="left">Product label</th>
</tr>
</thead>

<tbody>
<tr class="odd">
<td align="left">'01</td>
<td align="left">Live animals</td>
</tr>
<tr class="odd">
<td align="left">'02</td>
<td align="left">Meat and edible meat offal</td>
</tr>
<tr class="odd">
<td align="left">'03</td>
<td align="left">Fish and crustaceans, molluscs and other aquatic invertebrates</td>
</tr>
<tr class="odd">
<td align="left">'04</td>
<td align="left">Dairy produce; birds' eggs; natural honey; edible products of animal origin, not elsewhere ...</td>
</tr>

</tbody>
</table>

Table 3: Product look-up excel table

Regarding the variables included in these tables; definitions are as follows:

<table>
<thead>
<tr class="header">
<th align="center" colspan="2">ExportQuantity & ImportQuantity</th>
</tr>
</thead>
<tbody>
<tr class="odd">
<td align="left">Country</td>
<td align="left">Trade Partner of Turkey</td>
</tr>
<tr class="odd">
<td align="left">Product_Code</td>
<td align="left">Traded Product Code in 4 digit</td>
</tr>
<tr class="odd">
<td align="left">Product_Label</td>
<td align="left">Product Definition</td>
</tr>  
<tr class="odd">
<td align="left">Unit</td>
<td align="left">Metric of Quantity</td>
</tr>
<tr class="odd">
<td align="left">Quantity_2013</td>
<td align="left">Export or Import quantity in 2013</td>
</tr>
<tr class="odd">
<td align="left">Quantity_2014</td>
<td align="left">Export or Import quantity in 2014</td>
</tr>
<tr class="odd">
<td align="left">Quantity_2015</td>
<td align="left">Export or Import quantity in 2015</td>
</tr>
<tr class="odd">
<td align="left">Quantity_2016</td>
<td align="left">Export or Import quantity in 2016</td>
</tr>
<tr class="odd">
<td align="left">Quantity_2017</td>
<td align="left">Export or Import quantity in 2017</td>
</tr>  
</tbody>
</table>

<table>
<thead>
<tr class="header">
<th align="center" colspan="2">ExportValues & ImportValues</th>
</tr>
</thead>
<tbody>
<tr class="odd">
<td align="left">Country</td>
<td align="left">Trade Partner of Turkey</td>
</tr>
<tr class="odd">
<td align="left">Product_Code</td>
<td align="left">Traded Product Code in 4 digit</td>
</tr>
<tr class="odd">
<td align="left">Product_Label</td>
<td align="left">Product Definition</td>
</tr>  
<tr class="odd">
<td align="left">Value_2013</td>
<td align="left">Export or Import value in 2013</td>
</tr>
<tr class="odd">
<td align="left">Value_2014</td>
<td align="left">Export or Import value in 2014</td>
</tr>
<tr class="odd">
<td align="left">Value_2015</td>
<td align="left">Export or Import value in 2015</td>
</tr>
<tr class="odd">
<td align="left">Value_2016</td>
<td align="left">Export or Import value in 2016</td>
</tr>
<tr class="odd">
<td align="left">Value_2017</td>
<td align="left">Export or Import value in 2017</td>
</tr>
</tbody>
</table>

### Data Preparation, cleaning and Manipulation

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
```

In order to read these excel files, firstly we create a function named "getDataSet":

```{r, warning=FALSE}

PATH <-"C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/Raw Data"
setwd(PATH)

getDataSet <- function(pPattern){
  nm <- list.files(path = PATH, pattern = pPattern)  
  if (exists("resultDataset")){
    rm("resultDataset")
  }
  for (file in nm){
    if (!exists("resultDataset")){
      resultDataset <- read_excel(file, col_names=FALSE, skip=1)
    }
    else{
      temp_dataset <-read_excel(file, col_names=FALSE, skip=1)
      resultDataset<-rbind(resultDataset, temp_dataset)
      rm(temp_dataset)
    }

  }
  return(resultDataset)

}

import_quantity_dataset <- getDataSet('*.mport.*uant.*')
import_value_dataset <- getDataSet('*.mport.*alu.*')
export_quantity_dataset <- getDataSet('*.xport.*uant.*')
export_value_dataset <- getDataSet('*.xport.*alu.*')

colnames(import_quantity_dataset) <- c("Country","Product_Code","Product_Label","Quantity_2013","Unit1","Quantity_2014","Unit2","Quantity_2015","Unit3","Quantity_2016","Unit4","Quantity_2017","Unit5")
colnames(import_value_dataset) <- c("Country","Product_Code","Product_Label","Value_2013","Value_2014","Value_2015","Value_2016","Value_2017")
colnames(export_quantity_dataset) <- c("Country","Product_Code","Product_Label","Quantity_2013","Unit1","Quantity_2014","Unit2","Quantity_2015","Unit3","Quantity_2016","Unit4","Quantity_2017","Unit5")
colnames(export_value_dataset) <- c("Country","Product_Code","Product_Label","Value_2013","Value_2014","Value_2015","Value_2016","Value_2017")

import_quantity_dataset$Product_Code<- gsub("'", "", import_quantity_dataset$Product_Code)
import_value_dataset$Product_Code<- gsub("'", "",import_value_dataset$Product_Code)
export_quantity_dataset$Product_Code<- gsub("'", "",export_quantity_dataset$Product_Code)
export_value_dataset$Product_Code<- gsub("'", "",export_value_dataset$Product_Code)

```

And by using the getDataSet function, we merged the Turkey's export-quantity, export-value, import-quantity, import-value tables for 10 selected countries.

```{r}
glimpse(export_quantity_dataset)
glimpse(export_value_dataset)
glimpse(import_quantity_dataset)
glimpse(import_value_dataset)
```

We have 13 and 8 variables in quantity and value tables respectively both for export and import.

Now, it is time to join quantity and value data for both export and import files. While joining the tables, we should also clear the repetitive variable "Unit" for each year.

Also, we need to join product labels in 2 digit product codes to 4 digit product codes and labels.

```{r, warning=FALSE}
#read the ProductCodes excel
file = "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/2digitproductlist.xlsx"
prdCode <- read_excel(file, col_names=FALSE, skip=1)
prdCode$X__1 <- gsub("'", "", prdCode$X__1)

# join the import values and quantities
import_jTable <- import_quantity_dataset %>% 
  mutate( Unit= coalesce(Unit1,Unit2 ,Unit3 , Unit4,Unit5)) %>%
  select( Country, Product_Code , Unit, Quantity_2013, Quantity_2014, Quantity_2015, Quantity_2016, Quantity_2017) %>% 
  full_join(import_value_dataset,by = c("Country","Product_Code"))  
# seperate the first 2 digits of 4 digit product code and join the 2digit product code excel 
import_jTable <- import_jTable %>% mutate(PcodeTwo=substr(Product_Code,1,2))
import_jTable <- left_join(import_jTable,prdCode,by =c("PcodeTwo"="X__1") )

# join the export values and quantities
export_jTable <- export_quantity_dataset %>% 
  mutate( Unit= coalesce(Unit1,Unit2 ,Unit3 , Unit4,Unit5)) %>%
  select( Country, Product_Code , Unit, Quantity_2013, Quantity_2014,Quantity_2015,Quantity_2016,Quantity_2017) %>% 
  full_join(export_value_dataset,by = c("Country","Product_Code"))  
# seperate the first 2 digits of 4 digit product code and join the 2digit product code excel
export_jTable <- export_jTable %>% mutate(PcodeTwo=substr(Product_Code,1,2))
export_jTable <- left_join(export_jTable,prdCode,by =c("PcodeTwo"="X__1") )

```

Now we have joined tables for import and export stats of Turkey.

```{r}
glimpse(import_jTable)
glimpse(export_jTable)
```

Both tables now have 16 variables and 12,223 rows.

But there is a row in Product_Code column as "TOTAL", we must clear it.

```{r}
export_jTable <- export_jTable %>% filter(!grepl("TOTAL", Product_Code))
import_jTable <- import_jTable %>% filter(!grepl("TOTAL", Product_Code))
```

We have 16 variables in these tables however quantity and value variables repeat for each year. So actually, it is better to organize the table that it will have variables "Year", "Quantity", "Value" instead of 10 columns.

```{r}
#create new objects for each years' quantity
q2013<-import_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2013) %>% mutate(year="2013") %>% rename("Quantity"=Quantity_2013)
q2014<-import_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2014) %>% mutate(year="2014") %>% rename("Quantity"=Quantity_2014)
q2015<-import_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2015) %>% mutate(year="2015") %>% rename("Quantity"=Quantity_2015)
q2016<-import_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2016) %>% mutate(year="2016") %>% rename("Quantity"=Quantity_2016) 
q2017<-import_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2017) %>% mutate(year="2017") %>% rename("Quantity"=Quantity_2017)

#bind the objects
importQuant <- bind_rows(q2013,q2014,q2015,q2016,q2017)

#create new objects for each years' values
v2013<-import_jTable %>% select(Country,Product_Code, Value_2013) %>% rename("Values"=Value_2013) %>% mutate(year="2013")
v2014<-import_jTable %>% select(Country,Product_Code, Value_2014) %>% rename("Values"=Value_2014) %>% mutate(year="2014")
v2015<-import_jTable %>% select(Country,Product_Code, Value_2015) %>% rename("Values"=Value_2015) %>% mutate(year="2015")
v2016<-import_jTable %>% select(Country,Product_Code, Value_2016) %>% rename("Values"=Value_2016) %>% mutate(year="2016") 
v2017<-import_jTable %>% select(Country,Product_Code, Value_2017) %>% rename("Values"=Value_2017) %>% mutate(year="2017")

#bind the objects
importValues <- bind_rows(v2013,v2014,v2015,v2016,v2017)

#join binded quantity and value
import_jTableMELTED <- importQuant %>% left_join(importValues, by=c("Country","Product_Code","year"))

#Repeat with export table

q2013<-export_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2013) %>% mutate(year="2013") %>% rename("Quantity"=Quantity_2013)
q2014<-export_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2014) %>% mutate(year="2014") %>% rename("Quantity"=Quantity_2014)
q2015<-export_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2015) %>% mutate(year="2015") %>% rename("Quantity"=Quantity_2015)
q2016<-export_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2016) %>% mutate(year="2016") %>% rename("Quantity"=Quantity_2016) 
q2017<-export_jTable %>% select(Country, PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity_2017) %>% mutate(year="2017") %>% rename("Quantity"=Quantity_2017)

exportQuant <- bind_rows(q2013,q2014,q2015,q2016,q2017)

v2013<-export_jTable %>% select(Country,Product_Code, Value_2013) %>% rename("Values"=Value_2013) %>% mutate(year="2013")
v2014<-export_jTable %>% select(Country,Product_Code, Value_2014) %>% rename("Values"=Value_2014) %>% mutate(year="2014")
v2015<-export_jTable %>% select(Country,Product_Code, Value_2015) %>% rename("Values"=Value_2015) %>% mutate(year="2015")
v2016<-export_jTable %>% select(Country,Product_Code, Value_2016) %>% rename("Values"=Value_2016) %>% mutate(year="2016") 
v2017<-export_jTable %>% select(Country,Product_Code, Value_2017) %>% rename("Values"=Value_2017) %>% mutate(year="2017")

exportValues <- bind_rows(v2013,v2014,v2015,v2016,v2017)

export_jTableMELTED <- exportQuant %>% left_join(exportValues, by=c("Country","Product_Code","year"))
```

Now, we have more useful tables, with 9 variables and 61100 rows.

```{r}
glimpse(export_jTableMELTED)
glimpse(import_jTableMELTED)
```

### 2018-12-15 sourceCode/projeBusra.R
Update projeBusra.R

@@ -20,11 +20,12 @@ rm(githubURL_export)
 rm(githubURL_import)
 rm(githubURL_exportMELTED)
 rm(githubURL_importMELTED)
-
+print("=========")
 unit_price_import <- import_jTableMELTED %>% select(Country,PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity, year, Values) %>% mutate(Unit_Price = Values/Quantity)
+
 unit_price_export <- export_jTableMELTED %>% select(Country,PcodeTwo, X__2 ,Product_Code, Product_Label, Unit, Quantity, year, Values) %>% mutate(Unit_Price = Values/Quantity)
 unit_price_import$year <- as.numeric(as.character(unit_price_import$year))
-
+print(unit_price_import)
 
 country <- 
   import_jTableMELTED %>% 
@@ -58,8 +59,8 @@ ui <- fluidPage(
                   min = min(unit_price_import$year),
                   max = max(unit_price_import$year),
                   value = min(unit_price_import$year)),
-      selectInput(inputId =PcodeTwo,label = "Product Code",choices = c("All",PcodeTwo)),
-      checkboxGroupInput(inputId = country, label = "Countries",choices = c("All",country))
+      selectInput(inputId ="PcodeTwo",label = "Product Code",choices = c("All",PcodeTwo)),
+      checkboxGroupInput(inputId = "Country", label = "Countries",choices = c("All",country))
       
     ),
     
@@ -71,17 +72,18 @@ ui <- fluidPage(
 )
 
 # Define server logic required to draw a histogram
-server <- function(input, output) {
+server <- function(input, output,session) {
   
   output$distPlot <- renderPlot({
     modified_data <- unit_price_import #%>% filter(year == input$year & PcodeTwo == input$PcodeTwo)
-    
-    if(input$Country != "All"){
-      modified_data <- modified_data %>% filter(Country ==input$country)
+    print(input$Country)
+    if(input$Country[1] != "All"){
+      modified_data <- modified_data %>% filter(Country %in% input$Country)
     }
     print(modified_data)
-    ggplot(modified_data, aes(x=Country, y= Unit_Price
-    )) + geom_bar(stat="identity")
+    p1 <-
+    ggplot(modified_data, aes(x=Country, y= Unit_Price)) + geom_bar(stat="identity")
+    p1
   })
 }
 

### 2018-12-16 sourceCode/endeksOmer.R
son gelişmeler

@@ -1,0 +1,61 @@
+library(shiny)
+library(tidyverse)
+library(dplyr)
+library(readxl)
+library(lubridate)
+library(reshape2)
+
+
+
+usdR <- read_excel("C:/Users/avs1400/Desktop/master/DataAnEssR_503/project/EVDS.xlsx", col_names=FALSE, skip=1)
+#usdR <- read_excel("D:/OMER/master/BDA-503/EVDS.xlsx", col_names=FALSE, skip=1)
+
+colnames(usdR) <- c("DateR","ExchangeRate")
+usd <- na.omit(usdR)
+remove(usdR)
+
+usdN<-usd %>% mutate(Date=dmy(DateR))
+usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
+
+
+#bist100R <- read_excel("D:/OMER/master/BDA-503/BIST100.xlsx", col_names=FALSE, skip=1)
+bist100R <- read_excel("C:/Users/avs1400/Desktop/master/DataAnEssR_503/project/BIST100.xlsx", col_names=FALSE, skip=1)
+
+colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
+bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
+  group_by(Year) %>% 
+  summarise(Value = mean(Value)*1000)
+
+
+
+githubURL_export <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTable.rds?raw=true")
+githubURL_import <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTable.rds?raw=true")
+
+export_jTable<- readRDS(url(githubURL_export))
+import_jTable<- readRDS(url(githubURL_import))
+
+sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
[…]

### 2018-12-16 shiny/report.Rmd

---
title: "Turkey Trade Analysis Group Fou\\*R* Project"
author: "Group Fou\\*R* - BDA 503 - Fall 2018"
date: "7 December 2018"
output: 
  html_document:
    theme: yeti
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Group Members
[Büşra Koç](https://mef-bda503.github.io/pj18-busraakoc/) <br>
[Emre Kemerci](https://mef-bda503.github.io/pj18-EmreKemerci/)<br>
[Muharrem Çakır](https://mef-bda503.github.io/pj18-muharremcakir81/)<br>
[Ömer Bayır](https://mef-bda503.github.io/pj18-omerbayir/)<br>
[Salih Uçar](https://mef-bda503.github.io/pj18-ucarsal/)

## Data
Turkey's two way trade data between ten important country. The data has been obtained from [www.trademap.org](www.trademap.org) .
The site gives trade statistics for international business development. Gives import or export values and units yeraly
or quarterly.
The countries below choosen:

* Canada
* China
* France
* Germany
* India
* Italy
* Russian
* UK
* USA
* Japan

## Description
The Global Terrorism Database (GTD) includes information on terrorist events around the World (205 countries, more than 33000 cities, from 1970 through 2016 on at least 45 variables for each case, with more recent incidents including information on more than 120 variables
This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-12-16 Draft.Rmd
.

--- 2018-12-13 PreliminaryAnalysis.Rmd
@@
 
-We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey’s trade characteristics by product groups.
+We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey?s trade characteristics by product groups.
 Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017.
@@
 
-Following the extraction from source (Trademap.org), our raw data consist of 10 countries’ trade data against Turkey.
-This data splits to 2 with trade direction as “Export” and “Import”.
-The other dimension is stat for trade, one is “Quantity” of Export/Import, the other is “Value” in billion USD of Export/Import.
+Following the extraction from source (Trademap.org), our raw data consist of 10 countries?
+trade data against Turkey.
+This data splits to 2 with trade direction as ?Export?
+and ?Import?.
+The other dimension is stat for trade, one is ?Quantity?
+of Export/Import, the other is ?Value?
+in thousand USD of Export/Import.
 Therefore we have four main data frame for each country (total of 40 excel files).
@@
 <td align="left">ExportValues</td>
-<td align="left">Export from Turkey to target countries and their values in billion USD</td>
+<td align="left">Export from Turkey to target countries and their values in thousand USD</td>
 </tr>
@@
 <td align="left">ImportValues</td>
-<td align="left">Import to Turkey from target counties and their values in billion USD</td>
+<td align="left">Import to Turkey from target counties and their values in thousand USD</td>
 </tr>
@@
 library(leaflet)
+library(reshape2)
 ```
@@
 ```
+
+###Analysis
+
+####SALIH
+
+```{r}
+# Export Values in $ 
+ttable=export_jTableMELTED%>%group_by(Country,year)%>%
+  summarise(co_total=sum(Values,na.rm = TRUE))%>%
+  arrange(desc(co_total,year))
+
+```
+
+```{r}
+#Import Values in $
+vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))
+
+a<-ggplot(data=vtable, aes(x=Country, y=co_total,fill=year)) +
+  geom_bar(stat="identity", position=position_dodge(), colour="black")+
+  ggtitle("Total Import Values in $ to Selected Countries")
+
+#Export percentage of Countries
+
+b<-ggplot(data=ttable, aes(x=Country, y=co_total,fill=year)) +
+  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Total Export Values in $ to Selected Countries")
+
+grid.arrange(a,b,  nrow = 2)
+```
+
+#Import percentage Values in $
+
+pim_table<-vtable%>%filter(year=='2017')%>%
+  mutate(perc_count=co_total/sum((vtable%>%filter(year=='2017'))$co_total)*100)%>%
+  select(Country,year,co_total,perc_count)
+
+ggplot(pim_table, aes(x="", y=perc_count, fill=Country)) + geom_bar(stat="identity", width=1)+
+  coord_polar("y") + geom_text(aes(label = round(perc_count,1), "%"), position = position_stack(vjust = 0.5))+
+  labs(x = NULL, y = NULL, fill = NULL, title = "Percentage of Countries in Import in 2017")+theme_classic()+
+  theme(axis.text = element_blank(),plot.title = element_text(hjust = 0.5, color = "#666666"))
+
+####OMER
+
+In order to deeply understand the data; we build up shiny app with Country, Product and Year variables.
+
+Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrg)
+
+####MUHARREM
+####Analysis of Trade Deficit by Countries and Years
+
+To discovery that country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
+
+First, group data;
+
+```{r }
+export_Product_Group <- export_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
+
+import_Product_Group <- import_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
+
+Export_Import_JTable <- export_Product_Group %>%
+  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
+mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
+        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
+select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
+```
+
+Continue with visulation;
+
+```{r}
+####Net Value By Country###
+Net_Value_By_Country <- Export_Import_JTable %>%
+group_by(Country,year)%>%
+summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
+           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))
+
+# Total Net Value fiiled with Country on the basis of Year #
+ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
+  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
+  labs(subtitle="## Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
+  coord_flip()+
+  theme(legend.position = "top")
+```
+
+As seen in the graph, only UK gives trade surplus for all years analysed and China, Russia, Germany and USA have the most significant effect on trade deficit.
+
+##### An Alternative perspective to explore effects of countries
+
+The effects of countries are changing year by year.
+So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
+
+```{r }
+#Normalized of Average Values for five years
+Normalized_Values_By_Country <- Export_Import_JTable %>%
+  #filter (year == 2017)%>%
+  group_by(Country)%>%
+  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
+  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
+  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
+
+#Diverging Bars for normalized_Export_value
+ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
+  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
+  scale_fill_manual(name="Normalised Value", 
+                    labels = c("Above Average", "Below Average"), 
+                    values = c("above"="seagreen1", "below"="Red")) +  
+  labs(subtitle="Normalised Net Value for 5 years by Country'", 
+       title= "Diverging Bars") + 
+  coord_flip()
+```
+
+Considering the 5 years period, it is clear that China, Germany and Russia has contribution to trade deficit above average.
+
+In order to understand the correlation between trade deficit/surplus and BIST100 index and USD/TL rates, we added this economic indicators to our analysis:
+
+Read the USD and BIST100 index values and rename the columns
+
+```{r}
+fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
+usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)
+
+colnames(usdR) <- c("DateR","ExchangeRate")
+usd <- na.omit(usdR)
+remove(usdR)
+
+usdN<-usd %>% mutate(Date=dmy(DateR))
+usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
+
+fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
+bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)
+
+colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
+bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
+  group_by(Year) %>% 
+  summarise(Value = mean(Value)*1000)
+```
+
+Draw the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
+
+```{r}
+sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
+  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
+         Value_2017=Value_2017.y-Value_2017.x) %>%
+  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)
+
+joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
+deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
+                                                                       variable == "Value_2014" ~ 2014,
+                                                                       variable == "Value_2015" ~ 2015,
+                                                                       variable == "Value_2016" ~ 2016,
+                                                                       variable == "Value_2017" ~ 2017)) %>%
+  select(Country,year,value)
+
+deficitPerYear <- deficitPerCountry %>%
+  group_by(year) %>% summarise(value=sum(value))
+
+p<-ggplot() + 
+  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
+  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
+  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
+  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))
+
+print(p)
+
+```
+
+Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
+Besides, there is not a direct correlation between BIST100 index and Trade Deficit Values.
+
+####EMRE
+
+####Analysis of Year by Year Change in Trade Values
+
+```{r}
+tableExport <- export_jTableMELTED %>% 
+  group_by(Country, year) %>%
+  summarise(totalExpV=sum(Values,na.rm=TRUE)) %>%
+  arrange(Country, year) %>%
+  mutate(ExpValChng = (totalExpV - lag(totalExpV))/lag(totalExpV)*100)
+
+tableImport <- import_jTableMELTED %>% 
+  group_by(Country, year) %>%
+  summarise(totalImpV=sum(Values,na.rm=TRUE)) %>%
+  arrange(Country, year) %>%
+  mutate(ImpValChng = (totalImpV - lag(totalImpV))/lag(totalImpV)*100)
+
+table <- full_join(tableExport,tableImport) %>%
+  select(Country, year, Export="ExpValChng", Import = "ImpValChng") %>%
+  melt(id=c("Country", "year")) %>%
+  filter(year!=2013)
+```
+
+```{r}
+ggplot(table, aes(x=year)) +
+  geom_point(aes(y=value, color=Country, shape=variable), size=4) + 
+  facet_grid(~variable) +
+   labs(title="YoY Total Value Change",
+    x="Year",
+    y="% Change in  Value",
+    shape=c("Trade Type"))
+```
+
+```{r}
+
+# Canada and Russia significantly deviates. Investigate these countries in detail with traded products
+
+# First Canada
+
+# Export Analysis
+
+summarytableCanadaEx <- export_jTableMELTED %>%
+  filter(Country=="Canada") %>%
+  group_by(X__2, year) %>%
+  summarise(ExportValue=sum(Values)) %>%
+  arrange(X__2, year) %>%
+  mutate(ExpPercChngYoY = (ExportValue - lag(ExportValue))/lag(ExportValue)*100) %>%
+  mutate(ExpChngYoy=((ExportValue - lag(ExportValue)))) %>%
+  filter(year!=2013)
+
+mean(summarytableCanadaEx$ExpChngYoy)
+median(summarytableCanadaEx$ExpChngYoy)
+sd(summarytableCanadaEx$ExpChngYoy)
+quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
+altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - IQR
+ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + IQR
+
+summarytableCanadaEx <- summarytableCanadaEx %>%
+  filter(abs(ExpChngYoy)>max(abs(altsinir),ustsinir))
+
+plotCanEx <- ggplot(summarytableCanadaEx, aes(x=substr(X__2, start = 1, stop = 30))) +
+  geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  facet_grid (~year) +
+  facet_grid(rows = vars(year)) +
+  labs(title="YoY Total Value Change with Canada - Export",
+       x="Product Group",
+       y="Change in Export Value",
+       Color=c("Year"))
+
+# Import Analysis
+
+summarytableCanadaIm <- import_jTableMELTED %>%
+  filter(Country=="Canada") %>%
+  group_by(X__2, year) %>%
+  summarise(ImportValue=sum(Values)) %>%
+  arrange(X__2, year) %>%
+  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
+  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
+  filter(year!=2013)
+
+mean(summarytableCanadaIm$ImpChngYoy)
+median(summarytableCanadaIm$ImpChngYoy)
+sd(summarytableCanadaIm$ImpChngYoy)
+quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
+altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - IQR
+ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + IQR
+
+summarytableCanadaIm <- summarytableCanadaIm %>%
+  filter(abs(ImpChngYoy)>max(abs(altsinir),ustsinir))
+
+plotCanIm <- ggplot(summarytableCanadaIm, aes(x=substr(X__2, start = 1, stop = 30))) +
+  geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  facet_grid (~year) +
+  facet_grid(rows = vars(year)) +
+  labs(title="YoY Total Value Change Canada - Import",
+       x="Product Group",
+       y="Change in Import Value",
+       Color=c("Year"))
+```
+
+```{r}
+
+# Second Russia
+
+# Export Analysis
+
+summarytableRussianEx <- export_jTableMELTED %>%
+  filter(Country=="Russian") %>%
+  group_by(X__2, year) %>%
+  summarise(ExportValue=sum(Values)) %>%
+  arrange(X__2, year) %>%
+  mutate(ExpPercChngYoY = (ExportValue - lag(ExportValue))/lag(ExportValue)*100) %>%
+  mutate(ExpChngYoy=((ExportValue - lag(ExportValue)))) %>%
+  filter(year!=2013)
+
+mean(summarytableRussianEx$ExpChngYoy)
+median(summarytableRussianEx$ExpChngYoy)
+sd(summarytableRussianEx$ExpChngYoy)
+quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
+altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - IQR
+ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + IQR
+
+summarytableRussianEx <- summarytableRussianEx %>%
+  filter(abs(ExpChngYoy)>max(abs(altsinir),ustsinir))
+
+plotRusEx <- ggplot(summarytableRussianEx, aes(x=substr(X__2, start = 1, stop = 30))) +
+  geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  facet_grid (~year) +
+  facet_grid(rows = vars(year)) +
+  labs(title="YoY Total Value Change Russia - Export",
+       x="Product Group",
+       y="Change in Export Value",
+       Color=c("Year"))
+
+# Import Analysis
+
+summarytableRussianIm <- import_jTableMELTED %>%
+  filter(Country=="Russian") %>%
+  group_by(X__2, year) %>%
+  summarise(ImportValue=sum(Values)) %>%
+  arrange(X__2, year) %>%
+  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
+  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
+  filter(year!=2013)
+
+mean(summarytableRussianIm$ImpChngYoy)
+median(summarytableRussianIm$ImpChngYoy)
+sd(summarytableRussianIm$ImpChngYoy)
+quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
+altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - IQR
+ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + IQR
+
+summarytableRussianIm <- summarytableRussianIm %>%
+  filter(abs(ImpChngYoy)>max(abs(altsinir),ustsinir))
+
+plotRusIm <- ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 30))) +
+  geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  facet_grid (~year) +
+  facet_grid(rows = vars(year)) +
+  labs(title="YoY Total Value Change Russia - Import",
+       x="Product Group",
+       y="Change in Import Value",
+       Color=c("Year"))
+```
+
+```{r}
+
+#install.packages("gridExtra")
+
+library(gridExtra)
+
+grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
+grid.arrange(plotRusEx, plotRusIm,  nrow = 2)
+
+```

### 2018-12-16 sourceCode/Analysis_Data_Muh.Rmd

---
title: "Trademap_Data_Analysis"
author: "Muharrem Çakır"
date: "14 Aralık 2018"
output: html_document
---

## Define Libraries to use and get Data from github repository
First of all we define all package which are used for different aims below. After that we read four data sources which are stored as rds format in github and assigned to export_jTable, import_jTable,export_jTableMELTED, import_jTableMELTED respectively. 
we grouped data by 2 digit product code is named as 'Product Group Code' and summarize Quantity and value columns by country, year and  Product Group Code. 
```{r}

library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(ggplot2)

githubURL_export <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTable.rds?raw=true")
githubURL_import <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTable.rds?raw=true")
githubURL_exportMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTableMELTED.rds?raw=true")
githubURL_importMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTableMELTED.rds?raw=true")

export_jTable<- readRDS(url(githubURL_export))
import_jTable<- readRDS(url(githubURL_import))
export_jTableMELTED<- readRDS(url(githubURL_exportMELTED))
import_jTableMELTED<- readRDS(url(githubURL_importMELTED))

rm(githubURL_export)
rm(githubURL_import)
rm(githubURL_exportMELTED)
rm(githubURL_importMELTED)

export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)

import_Product_Group <- import_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)

Export_Import_JTable <- export_Product_Group %>%
  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
```

## Calculate Net_Value basis Country and year

To discovery that counrty's effects to current deficit we calculate net_value which formule is 'Export_value - Import_value'. And visualize that value on the basis of year

```{r}
####Net Value By Country###
Net_Value_By_Country <- Export_Import_JTable %>%
group_by(Country,year)%>%
summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))

# Total Net Value fiiled with Country on the basis of Year #
ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
  labs(subtitle="## Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
  coord_flip()+
  theme(legend.position = "top")
```

## An Alternative perspective to explore effects of countries

The effects of countries may be change year by year. So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
It is clear that China,Germany and Russia are more effect than others.
```{r }
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  #filter (year == 2017)%>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

#Diverging Bars for normalized_Export_value
ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
  scale_fill_manual(name="Normalised Value", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="seagreen1", "below"="Red")) +  
  labs(subtitle="Normalised Net Value for 5 years by Country'", 
       title= "Diverging Bars") + 
  coord_flip()
```
## Most effective products which increase import values

```{r}
Import_Value_by_product <- import_Product_Group %>%
  filter (Country %in% c("China","Germany","Russian"))%>%
  group_by(Country,Product_Group_Code,Product_Group_Name)%>%
  summarize (Average_Import_Value = mean(Import_Value))

Import_Value_by_product<- Import_Value_by_product %>%
  group_by(Country)%>%
  mutate(Total_Average_Import_Value = sum(Average_Import_Value))

Import_Value_by_product <- Import_Value_by_product %>%
  mutate(Average_Import_pct = round((Average_Import_Value / Total_Average_Import_Value)*100,2))%>% 
  arrange(Country,desc(Average_Import_pct))

Import_Value_by_product<- Import_Value_by_product %>%
  group_by(Country) %>% 
  mutate(Cum_Import_Pct = cumsum(Average_Import_pct)) %>%
  filter (Cum_Import_Pct <= 70)

```

### 2018-12-16 sourceCode/Analysis_Data_Muh.Rmd

@@
 group_by(Country,PcodeTwo,X__2,year)%>%
-summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
-rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
+summarize(Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Value =Values)
 
@@
 Normalized_Values_By_Country <- Export_Import_JTable %>%
-  #filter (year == 2017)%>%
   group_by(Country)%>%
@@
 ```{r}
+Normalized_Values_By_Country <- Export_Import_JTable %>%
+  group_by(Country)%>%
+  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
+  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
+  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
+
+Country_type <- Normalized_Values_By_Country%>%
+   select( Country, value_Net_type)
+
+import_Product_Group  <- import_Product_Group %>%
+left_join(Country_type,value_Net_type,by = "Country")
+
 Import_Value_by_product <- import_Product_Group %>%
-  filter (Country %in% c("China","Germany","Russian"))%>%
+  filter (value_Net_type == "below" )%>%
   group_by(Country,Product_Group_Code,Product_Group_Name)%>%
@@
   group_by(Country) %>% 
-  mutate(Cum_Import_Pct = cumsum(Average_Import_pct)) %>%
-  filter (Cum_Import_Pct <= 70)
+  mutate(Cum_Import_Pct = cumsum(Average_Import_pct))
 

### 2018-12-16 Draft.Rmd
.

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
 library(shiny)
@@
 library(reshape2)
+library(gridExtra)
+library(lubridate)
+library(plotrix)
 ```
@@
 ```{r}
+
+```
+
+```{r}
+ttable1=export_jTableMELTED%>%group_by(Country)%>%
+  summarise(co_total=sum(Values,na.rm = TRUE))%>%
+  arrange(desc(co_total,year))
+
+exptable1=export_jTableMELTED%>%group_by(Country)%>%
+  summarise(co_total=sum(Values,na.rm = TRUE))%>%
+  arrange(desc(co_total,year))
+
+pex1_table<-ttable1%>%
+  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+  select(Country,co_total,perc_count)
+
+imptable1=import_jTableMELTED%>%group_by(Country)%>%
+  summarise(co_total=sum(Values,na.rm = TRUE))%>%
+  arrange(desc(co_total,year))
+
+pim1_table<-imptable1%>%
+  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+  select(Country,co_total,perc_count)
+
+lbls_i <- paste(pim1_table$Country,round(pim1_table$perc_count,1)) # add percents to labels
+lbls_i <- paste(lbls_i,"%",sep="") # ad % to labels
+
+pie3D(pim1_table$perc_count,labels=lbls_i,main = "Total Percentage Import Per Countries", explode=0.1, radius=.9,
+      labelcex = 1.2, start=0.7)
+
+lbls_e <- paste(pex1_table$Country,round(pex1_table$perc_count,1)) # add percents to labels
+lbls_e <- paste(lbls_e,"%",sep="") # ad % to labels
+
+pie3D(pex1_table$perc_count,labels=lbls_e,main = "Total Percentage Export Per Countries", explode=0.1, radius=.9,
+             labelcex = 1.2, start=0.7)
+
+```
+
+```{r}
 # Export Values in $ 
@@
   arrange(desc(co_total,year))
-
-```
-
-```{r}
 #Import Values in $
 vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))
+
+#Import & Export percentage of Countries
 
@@
   ggtitle("Total Import Values in $ to Selected Countries")
-
-#Export percentage of Countries
 
@@
 
+We drilled down the analysis for the countries which decreases the average, namely China, Russia and Germany.
+For this aim, we build up shiny app to review the products by defining the Country and ratio showing cumulative percentage of share of products over total import value of this country.
+
+Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)
+
+Through the shiny app, it is understood that
+.70% of import value from China is coming from 8 products 
+.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
+.%70 is from commodities and mineral fuels for import from Russia
+.only commodities constitute 43% of total import of Russia
+.vehicles other than railway is the top product imported from Germany
+.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
+
+IMAGE
+
+###OMER2
+
 In order to understand the correlation between trade deficit/surplus and BIST100 index and USD/TL rates, we added this economic indicators to our analysis:
@@
 
-```{r}
+```{r, }
 ggplot(table, aes(x=year)) +
@@
 IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - IQR
-ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + IQR
+altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
+ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)
 
@@
 IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - IQR
-ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + IQR
+altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
+ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)
 
@@
 IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - IQR
-ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + IQR
+altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
+ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)
 
@@
 IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - IQR
-ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + IQR
+altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
+ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)
 
@@
 
-```{r}
+```{r, fig.height = 8, fig.width = 16}
 
@@
 grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
-grid.arrange(plotRusEx, plotRusIm,  nrow = 2)
+grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
 

### 2018-12-16 Draft.Rmd
.

@@
 ---
-title: "Group Fou\\*R* Term Project - Summary of Raw Data, Explanations and Preliminary Analysis"
+title: "Group Fou\\*R* Term Project"
 subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
@@
 
-### Data Preparation, cleaning and Manipulation
+### Data Preparation, Cleaning and Manipulation
 
@@
 
-###Analysis
+### Analysis
 
-####SALIH
-
-```{r}
-
-```
+#### Breakdown of Total Export and Import of Turkey Over Countries
 
@@
 
+At import side, Turkeys' biggest trade partners are China, Germany, Russia and US while they are Germany, UK, Italy and USA at export side.
+Germany and USA are the 2 countries exist for both type of trade.
+
+When we breakdown this info to years:
+
 ```{r}
@@
 
-#Import percentage Values in $
+Except Russia, fluctuates over years are not seem so significant.
 
-pim_table<-vtable%>%filter(year=='2017')%>%
-  mutate(perc_count=co_total/sum((vtable%>%filter(year=='2017'))$co_total)*100)%>%
-  select(Country,year,co_total,perc_count)
-
-ggplot(pim_table, aes(x="", y=perc_count, fill=Country)) + geom_bar(stat="identity", width=1)+
-  coord_polar("y") + geom_text(aes(label = round(perc_count,1), "%"), position = position_stack(vjust = 0.5))+
-  labs(x = NULL, y = NULL, fill = NULL, title = "Percentage of Countries in Import in 2017")+theme_classic()+
-  theme(axis.text = element_blank(),plot.title = element_text(hjust = 0.5, color = "#666666"))
-
-####OMER
-
-In order to deeply understand the data; we build up shiny app with Country, Product and Year variables.
+In order to deeply understand the data; we build up shiny app with Country, Product and Year variables to review export and import values.
 
@@
 
-####MUHARREM
-####Analysis of Trade Deficit by Countries and Years
+##### YORUM VE IMAGE EKLENECEK
 
-To discovery that country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
-
-First, group data;
-
-```{r }
-export_Product_Group <- export_jTableMELTED%>%
-group_by(Country,PcodeTwo,X__2,year)%>%
-summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
-rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
-
-import_Product_Group <- import_jTableMELTED%>%
-group_by(Country,PcodeTwo,X__2,year)%>%
-summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
-rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
-
-Export_Import_JTable <- export_Product_Group %>%
-  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
-mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
-        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
-select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
-```
-
-Continue with visulation;
-
-```{r}
-####Net Value By Country###
-Net_Value_By_Country <- Export_Import_JTable %>%
-group_by(Country,year)%>%
-summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
-           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))
-
-# Total Net Value fiiled with Country on the basis of Year #
-ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
-  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
-  labs(subtitle="## Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
-  coord_flip()+
-  theme(legend.position = "top")
-```
-
-As seen in the graph, only UK gives trade surplus for all years analysed and China, Russia, Germany and USA have the most significant effect on trade deficit.
-
-##### An Alternative perspective to explore effects of countries
-
-The effects of countries are changing year by year.
-So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
-
-```{r }
-#Normalized of Average Values for five years
-Normalized_Values_By_Country <- Export_Import_JTable %>%
-  #filter (year == 2017)%>%
-  group_by(Country)%>%
-  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
-  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
-  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
-
-#Diverging Bars for normalized_Export_value
-ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
-  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
-  scale_fill_manual(name="Normalised Value", 
-                    labels = c("Above Average", "Below Average"), 
-                    values = c("above"="seagreen1", "below"="Red")) +  
-  labs(subtitle="Normalised Net Value for 5 years by Country'", 
-       title= "Diverging Bars") + 
-  coord_flip()
-```
-
-Considering the 5 years period, it is clear that China, Germany and Russia has contribution to trade deficit above average.
-
-We drilled down the analysis for the countries which decreases the average, namely China, Russia and Germany.
-For this aim, we build up shiny app to review the products by defining the Country and ratio showing cumulative percentage of share of products over total import value of this country.
-
-Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)
-
-Through the shiny app, it is understood that
-.70% of import value from China is coming from 8 products 
-.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
-.%70 is from commodities and mineral fuels for import from Russia
-.only commodities constitute 43% of total import of Russia
-.vehicles other than railway is the top product imported from Germany
-.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
-
-IMAGE
-
-###OMER2
-
-In order to understand the correlation between trade deficit/surplus and BIST100 index and USD/TL rates, we added this economic indicators to our analysis:
-
-Read the USD and BIST100 index values and rename the columns
-
-```{r}
-fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
-usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)
-
-colnames(usdR) <- c("DateR","ExchangeRate")
-usd <- na.omit(usdR)
-remove(usdR)
-
-usdN<-usd %>% mutate(Date=dmy(DateR))
-usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
-
-fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
-bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)
-
-colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
-bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
-  group_by(Year) %>% 
-  summarise(Value = mean(Value)*1000)
-```
-
-Draw the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
-
-```{r}
-sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
-sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
-joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
-  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
-         Value_2017=Value_2017.y-Value_2017.x) %>%
-  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)
-
-joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
-deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
-                                                                       variable == "Value_2014" ~ 2014,
-                                                                       variable == "Value_2015" ~ 2015,
-                                                                       variable == "Value_2016" ~ 2016,
-                                                                       variable == "Value_2017" ~ 2017)) %>%
-  select(Country,year,value)
-
-deficitPerYear <- deficitPerCountry %>%
-  group_by(year) %>% summarise(value=sum(value))
-
-p<-ggplot() + 
-  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
-  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
-  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
-  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))
-
-print(p)
-
-```
-
-Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
-Besides, there is not a direct correlation between BIST100 index and Trade Deficit Values.
-
-####EMRE
-
-####Analysis of Year by Year Change in Trade Values
+#### Analysis of Year by Year Change in Trade Values
 
@@
        Color=c("Year"))
+```
 
+```{r, echo=FALSE}
 # Import Analysis
@@
 
-```{r}
+```{r, echo=FALSE}
 
@@
 ```
+
+#### Analysis of Trade Deficit by Countries and Years
+
+To discovery that country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
+
+First, group data;
+
+```{r }
+export_Product_Group <- export_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
+
+import_Product_Group <- import_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
+
+Export_Import_JTable <- export_Product_Group %>%
+  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
+mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
+        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
+select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
+```
+
+Continue with visulation;
+
+```{r}
+####Net Value By Country###
+Net_Value_By_Country <- Export_Import_JTable %>%
+group_by(Country,year)%>%
+summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
+           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))
+
+# Total Net Value fiiled with Country on the basis of Year #
+ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
+  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
+  labs(subtitle="Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
+  coord_flip()+
+  theme(legend.position = "top")
+```
+
+As seen in the graph, only UK gives trade surplus for all years analysed and China, Russia, Germany and USA have the most significant effect on trade deficit.
+
+##### An Alternative perspective to explore effects of countries
+
+The effects of countries are changing year by year.
+So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
+
+```{r }
+#Normalized of Average Values for five years
+Normalized_Values_By_Country <- Export_Import_JTable %>%
+  #filter (year == 2017)%>%
+  group_by(Country)%>%
+  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
+  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
+  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
+
+#Diverging Bars for normalized_Export_value
+ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
+  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
+  scale_fill_manual(name="Normalised Value", 
+                    labels = c("Above Average", "Below Average"), 
+                    values = c("above"="seagreen1", "below"="Red")) +  
+  labs(subtitle="Normalised Net Value for 5 years by Country'", 
+       title= "Diverging Bars") + 
+  coord_flip()
+```
+
+Considering the 5 years period, it is clear that China, Germany and Russia has contribution to trade deficit above average.
+
+We drilled down the analysis for the countries which decreases the average, namely China, Russia and Germany.
+For this aim, we build up shiny app to review the products by defining the Country and ratio showing cumulative percentage of share of products over total import value of this country.
+
+Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)
+
+Through the shiny app, it is understood that
+.70% of import value from China is coming from 8 products 
+.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
+.%70 is from commodities and mineral fuels for import from Russia
+.only commodities constitute 43% of total import of Russia
+.vehicles other than railway is the top product imported from Germany
+.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
+
+##### IMAGE EKLENECEK
+
+#### Correlation of Trade Deficit with FX Rate and BIST100 index
+
+In order to understand the correlation between trade deficit/surplus and BIST100 index and USD/TL rates, we added this economic indicators to our analysis:
+
+Read the USD and BIST100 index values and rename the columns
+
+```{r}
+fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
+usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)
+
+colnames(usdR) <- c("DateR","ExchangeRate")
+usd <- na.omit(usdR)
+remove(usdR)
+
+usdN<-usd %>% mutate(Date=dmy(DateR))
+usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
+
+fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
+bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)
+
+colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
+bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
+  group_by(Year) %>% 
+  summarise(Value = mean(Value)*1000)
+```
+
+Draw the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
+
+```{r}
+sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
+  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
+         Value_2017=Value_2017.y-Value_2017.x) %>%
+  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)
+
+joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
+deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
+                                                                       variable == "Value_2014" ~ 2014,
+                                                                       variable == "Value_2015" ~ 2015,
+                                                                       variable == "Value_2016" ~ 2016,
+                                                                       variable == "Value_2017" ~ 2017)) %>%
+  select(Country,year,value)
+
+deficitPerYear <- deficitPerCountry %>%
+  group_by(year) %>% summarise(value=sum(value))
+
+p<-ggplot() + 
+  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
+  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
+  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
+  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))
+
+print(p)
+
+```
+
+Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
+Besides, there is not a direct correlation between BIST100 index and Trade Deficit Values.

### 2018-12-16 Draft.Rmd
.

@@
 date: "December 2018"
-output: html_document
+output:
+  html_document:
+    toc: true
+    toc_float:
+      collapsed: true
+      smooth_scroll: false
+    number_sections: false
+    df_print: paged
+    code_folding: hide
+
 ---
-## Explanatory Data Analysis of Trade Statistics of Turkey
+# Explanatory Data Analysis of Trade Statistics of Turkey {.tabset .tabset-fade .tabset-pills}
 
-### Abstract
+## Abstract
 
-We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey?s trade characteristics by product groups.
+We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey's trade characteristics by product groups.
 Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017.
@@
 
-### Explanation of Raw Data
+## Explanation of Raw Data
 
-Following the extraction from source (Trademap.org), our raw data consist of 10 countries?
-trade data against Turkey.
-This data splits to 2 with trade direction as ?Export?
-and ?Import?.
-The other dimension is stat for trade, one is ?Quantity?
-of Export/Import, the other is ?Value?
-in thousand USD of Export/Import.
+Following the extraction from source (Trademap.org), our raw data consist of 10 countries' trade data against Turkey.
+This data splits to 2 with trade direction as 'Export' and 'Import'.
+The other dimension is stat for trade, one is 'Quantity' of Export/Import, the other is 'Value' in thousand USD of Export/Import.
 Therefore we have four main data frame for each country (total of 40 excel files).
@@
 
-### Data Preparation, Cleaning and Manipulation
+## Data Preparation, Cleaning and Manipulation
 
@@
 
-### Analysis
+## Analysis
 
-#### Breakdown of Total Export and Import of Turkey Over Countries
+### Breakdown of Total Export and Import of Turkey Over Countries
 
@@
 
-##### YORUM VE IMAGE EKLENECEK
+#### YORUM VE IMAGE EKLENECEK
 
-#### Analysis of Year by Year Change in Trade Values
+### Analysis of Year by Year Change in Trade Values
 
@@
 
-mean(summarytableCanadaEx$ExpChngYoy)
-median(summarytableCanadaEx$ExpChngYoy)
-sd(summarytableCanadaEx$ExpChngYoy)
-quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+#mean(summarytableCanadaEx$ExpChngYoy)
+#median(summarytableCanadaEx$ExpChngYoy)
+#sd(summarytableCanadaEx$ExpChngYoy)
+#quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
 IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
-ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)
+altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (2*IQR)
+ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (2*IQR)
 
@@
 
-mean(summarytableCanadaIm$ImpChngYoy)
-median(summarytableCanadaIm$ImpChngYoy)
-sd(summarytableCanadaIm$ImpChngYoy)
-quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+#mean(summarytableCanadaIm$ImpChngYoy)
+#median(summarytableCanadaIm$ImpChngYoy)
+#sd(summarytableCanadaIm$ImpChngYoy)
+#quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
 IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
-ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)
+altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (2*IQR)
+ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (2*IQR)
 
@@
 
-mean(summarytableRussianEx$ExpChngYoy)
-median(summarytableRussianEx$ExpChngYoy)
-sd(summarytableRussianEx$ExpChngYoy)
-quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+#mean(summarytableRussianEx$ExpChngYoy)
+#median(summarytableRussianEx$ExpChngYoy)
+#sd(summarytableRussianEx$ExpChngYoy)
+#quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
 IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
-ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)
+altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (2*IQR)
+ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (2*IQR)
 
@@
 
-mean(summarytableRussianIm$ImpChngYoy)
-median(summarytableRussianIm$ImpChngYoy)
-sd(summarytableRussianIm$ImpChngYoy)
-quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
+#mean(summarytableRussianIm$ImpChngYoy)
+#median(summarytableRussianIm$ImpChngYoy)
+#sd(summarytableRussianIm$ImpChngYoy)
+#quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
 IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
-altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
-ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)
+altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (2*IQR)
+ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (2*IQR)
 
@@
 
-```{r, fig.height = 8, fig.width = 16}
+```{r, echo=FALSE, fig.height=7, fig.width=10 }
 
-#install.packages("gridExtra")
+plotCanEx
+plotCanIm
+plotRusEx
+plotRusIm
 
-library(gridExtra)
-
-grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
-grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
-
+#grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
+#grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
+#fig.height=8, fig.width=16
 ```
 
-#### Analysis of Trade Deficit by Countries and Years
+### Analysis of Trade Deficit by Countries and Years
 
@@
 
-##### An Alternative perspective to explore effects of countries
+#### An Alternative perspective to explore effects of countries
 
@@
 Through the shiny app, it is understood that
-.70% of import value from China is coming from 8 products 
-.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
-.%70 is from commodities and mineral fuels for import from Russia
-.only commodities constitute 43% of total import of Russia
-.vehicles other than railway is the top product imported from Germany
-.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
+* 70% of import value from China is coming from 8 products 
+* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
+* %70 is from commodities and mineral fuels for import from Russia
+* Only commodities constitute 43% of total import of Russia
+* Vehicles other than railway is the top product imported from Germany
+* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
 
-##### IMAGE EKLENECEK
+#### IMAGE EKLENECEK
 
-#### Correlation of Trade Deficit with FX Rate and BIST100 index
+### Correlation of Trade Deficit with FX Rate and BIST100 index
 

### 2018-12-16 Draft.Rmd
.

@@
 Through the shiny app, it is understood that
+
 * 70% of import value from China is coming from 8 products 

### 2018-12-18 Draft/Draft20181218.Rmd
.

--- 2018-12-16 Draft.Rmd
@@
 ---
-title: "Group Fou\\*R* Term Project"
-subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
+title: "Explanatory Data Analysis of Trade Statistics of Turkey"
+subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
 date: "December 2018"
@@
 ---
-# Explanatory Data Analysis of Trade Statistics of Turkey {.tabset .tabset-fade .tabset-pills}
+# {.tabset .tabset-fade .tabset-pills}
 
@@
 
-We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey's trade characteristics by product groups.
-Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017.
-In this study, We applied data manipulation to make it proper for analysis and explanatory data analysis with visulations and conclude with overall statistical overview of Turkey's trade.
+In this term project, trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) is analysed.
+The aim of the project is to analyze Turkey's export and import characteristics by product groups considering the trade value and quantities.
+Within this aim, we take trade values and quantities by product groups in MS Excel file format from [trademap.org](https://trademap.org/Index.aspx) website for each trade partner for the period between 2013 and 2017.
+In this study, We followed the steps of explanation of raw data, preparation of raw data through merging the raw data files, cleaning, and manipulating,  analysing the data to explore the trade characteristics along with visulations and lastly concluding the comments from analysis.
 
@@
 
-Following the extraction from source (Trademap.org), our raw data consist of 10 countries' trade data against Turkey.
-This data splits to 2 with trade direction as 'Export' and 'Import'.
-The other dimension is stat for trade, one is 'Quantity' of Export/Import, the other is 'Value' in thousand USD of Export/Import.
-Therefore we have four main data frame for each country (total of 40 excel files).
+Following the extraction from source [(Trademap.org)](https://trademap.org/Index.aspx), our raw data consist of 10 countries' trade data against Turkey.
+This data split with trade direction as 'Export' and 'Import', in other words each country has 2 files as export and import.
+The other dimension is trade data; one is 'Quantity' of Export/Import, the other is 'Value' in thousand USD of Export/Import, which means each country has one file for 'Quantity' and one file for 'Trade Value'.
+Therefore we have four main data table for each country (total of 40 excel files).
 
@@
 
-Table structures for "Quantity" and "Value" files are as follows:
+Variables in "Quantity" and "Value" files are as follows:
 
@@
 
-Table 1: Quantity excel table structure
-
 <table>
@@
 
-Table 2: Values excel table structure
-
-In addition to main raw data, we also have look-up table for product codes; This lookup table registers product labels in 2 digit code that is less categorized than main data.
+In addition to main raw data, we also have a look-up table for product codes. This lookup table registers product labels in 2 digits code that is less categorized than main data.
 
@@
 </tr>
-<tr class="odd">
-<td align="left">'03</td>
-<td align="left">Fish and crustaceans, molluscs and other aquatic invertebrates</td>
-</tr>
-<tr class="odd">
-<td align="left">'04</td>
-<td align="left">Dairy produce; birds' eggs; natural honey; edible products of animal origin, not elsewhere ...</td>
-</tr>
 
@@
 </table>
-
-Table 3: Product look-up excel table
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
+We started with loading the needed libraries for preparation, manipulation, analysis and visualisation.  
+```{r, message=FALSE, warning=FALSE}
 library(shiny)
@@
 library(plotrix)
+library(treemap)
 ```
 
-In order to read these excel files, firstly we create a function named "getDataSet":
+First of all, we need to read the excel files constituting our raw data. For this aim, we wrote a function named "getDataSet".
 
@@
 
+```
+
+This function reads the excel files in the defined path according to given pattern in the filename and bind them in one file named "resultDataset".
+By using the getDataSet function, we merged the Turkey's export-quantity, export-value, import-quantity and import-value tables for 10 selected countries.
+
+Then, we named the columns and removed the single quotation marks in product code column in each file.
+
+```{r}
 colnames(import_quantity_dataset) <- c("Country","Product_Code","Product_Label","Quantity_2013","Unit1","Quantity_2014","Unit2","Quantity_2015","Unit3","Quantity_2016","Unit4","Quantity_2017","Unit5")
@@
 
-And by using the getDataSet function, we merged the Turkey's export-quantity, export-value, import-quantity, import-value tables for 10 selected countries.
+After the first step, the view of export & import quantity and export& import value datasets are below in respective order:
 
@@
 glimpse(export_quantity_dataset)
+glimpse(import_quantity_dataset)
 glimpse(export_value_dataset)
-glimpse(import_quantity_dataset)
 glimpse(import_value_dataset)
@@
 
-We have 13 and 8 variables in quantity and value tables respectively both for export and import.
+We have 13 and 8 variables in quantity and value tables respectively for export and import.
 
@@
 
-Also, we need to join product labels in 2 digit product codes to 4 digit product codes and labels.
+Also, we need to join product labels in 2 digit product codes with these table.
 
-```{r, warning=FALSE}
+```{r, echo=TRUE, warning=FALSE}
 #read the ProductCodes excel
@@
 
-Now we have joined tables for import and export stats of Turkey.
+Now we have joined tables for import and export stats of Turkey. Lets glimpse them:
 
@@
 
-But there is a row in Product_Code column as "TOTAL", we must clear it.
+But there is a row in Product_Code column as "TOTAL", we cleared it as well.
 
-```{r}
+```{r, echo=TRUE}
 export_jTable <- export_jTable %>% filter(!grepl("TOTAL", Product_Code))
@@
 We have 16 variables in these tables however quantity and value variables repeat for each year.
-So actually, it is better to organize the table that it will have variables "Year", "Quantity", "Value" instead of 10 columns.
+So actually, it is better to organize the table that it will have 3 variables as "Year", "Quantity" and "Value" instead of 10 columns.
 
@@
 
-Now, we have more useful tables, with 9 variables and 61100 rows.
+After above coding, now we have more useful tables, with 9 variables and 61100 rows.
 
@@
 
+These tables are ready for analysis that will be conducted in the next section. However, before proceeding first lets check the summary of export and import tables.
+
+```{r}
+summary(export_jTableMELTED)
+sd(export_jTableMELTED$Values)
+
+summary(import_jTableMELTED)
+sd(import_jTableMELTED$Values)
+```
+Since the quantities have different respective units, it is not logical to comment on descriptive statistics for quantity but for the values column we can say that the values are so dispersed with 4391 mean value and  36438 standart deviation for exports and 9495 mean and 110904 standart deviation.
+
 ## Analysis
@@
 
-```{r}
-ttable1=export_jTableMELTED%>%group_by(Country)%>%
-  summarise(co_total=sum(Values,na.rm = TRUE))%>%
-  arrange(desc(co_total,year))
+Our analysis starts with to understandthe shares of trade volume of the selected 10 countries on Turkey's import and export.
+
+```{r, fig.align="center"}
+# TREEMAP FOR EXPORT
 
@@
 
-pex1_table<-ttable1%>%
-  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+pex1_table<-exptable1%>%
+  mutate(perc_count=(co_total/sum(exptable1$co_total))*100)%>%
   select(Country,co_total,perc_count)
+
+treemap(pex1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Export Percentage on Countries",
+        fontsize.title = 17,type="value",palette = "Set1")
+
+# TREEMAP FOR IMPORT
 
@@
 pim1_table<-imptable1%>%
-  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+  mutate(perc_count=(co_total/sum(imptable1$co_total))*100)%>%
   select(Country,co_total,perc_count)
 
-lbls_i <- paste(pim1_table$Country,round(pim1_table$perc_count,1)) # add percents to labels
-lbls_i <- paste(lbls_i,"%",sep="") # ad % to labels
-
-pie3D(pim1_table$perc_count,labels=lbls_i,main = "Total Percentage Import Per Countries", explode=0.1, radius=.9,
-      labelcex = 1.2, start=0.7)
-
-lbls_e <- paste(pex1_table$Country,round(pex1_table$perc_count,1)) # add percents to labels
-lbls_e <- paste(lbls_e,"%",sep="") # ad % to labels
-
-pie3D(pex1_table$perc_count,labels=lbls_e,main = "Total Percentage Export Per Countries", explode=0.1, radius=.9,
-             labelcex = 1.2, start=0.7)
-
+treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
+        fontsize.title = 17,type="value",palette = "Set1")
 ```
 
-At import side, Turkeys' biggest trade partners are China, Germany, Russia and US while they are Germany, UK, Italy and USA at export side.
-Germany and USA are the 2 countries exist for both type of trade.
+As seen above, Turkeys' biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side.
+Germany and USA are the 2 top countries seen in both directions of trade.
 
-When we breakdown this info to years:
+When we breakdown this info to years, it is seen in below graphs that except Russia, fluctuations over years are not seem so significant but it is worth to deep dive Year over Year (YoY) changes.
 
-```{r}
+```{r, fig.align="center"}
 # Export Values in $ 
@@
 
-Except Russia, fluctuates over years are not seem so significant.
+### Analysis of Year over Year Changes in Trade Values
 
-In order to deeply understand the data; we build up shiny app with Country, Product and Year variables to review export and import values.
+In order to review YoY changes, we calculated delta of trade value for consecutive years and plotted as below seperating export and import.
 
-Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrg)
-
-#### YORUM VE IMAGE EKLENECEK
-
-### Analysis of Year by Year Change in Trade Values
-
-```{r}
+```{r, message=FALSE}
 tableExport <- export_jTableMELTED %>% 
@@
 
-```{r, }
+```{r, fig.align="center"}
 ggplot(table, aes(x=year)) +
@@
 
-```{r}
+From the graph, it is observable that especially in the years of 2015, 2016 and 2017 exports from Russia and Canada deviates strongly, up to above %50.
+And for the import side, again in 2016 and 2017 seems that Russia and Canada are top deviators and suprisingly in 2017 imports from Canada rises more than 100%.
+
+So, we should check which products drives these fluctuations.
+In order to visualize it, we found the highest delta products through filtering the ones exceeding 2 interquantile range (IQR - the difference between third and first quantile).
+
+```{r, fig.align="center"}
 
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, fig.align="center"}
 # Import Analysis
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, fig.align="center"}
 
@@
 
-```{r, echo=FALSE, fig.height=7, fig.width=10 }
+```{r, echo=FALSE, fig.height=7, fig.width=10, fig.align="center"}
 
@@
 
+It is concluded in above graphs that;
+
+* The observations of change of export to Canada in 2015 and 2017 are due to export of "Iron and Steel".
+* The observation of change of import from Canada in 2017 is due to import of "Natural or cultured pearls...".
+* The decrease in export to Russia in 2015 drives by "Vehicles other than railway..".
+* The decrease in export to Russia in 2016 and increase in 2017 is the effect of "Edible fruits and vegetables".
+* Imports from Russia deviates due to "Commodities not elsewhere speecified".
+
+Besides this analysis, we can discover more on this topic with different perspectives.
+To do this, we decided to build up shiny app with dependents of Country, Product and Year.
+Please follow the link to access to Shiny app.
+__[Link](https://groupfour.shinyapps.io/tradeOrg)__
+
+![Edible vegetable export to Russia](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\imageShiny1.png)
+
+This image taken from Shiny app and presents the trade values of edible vegetables over years. It is observable that, in 2016 Turkey's edible vegetable export to Russia dramatically downs.
+
+![Russian sanctions to Turkey](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\Capture.png)
+
 ### Analysis of Trade Deficit by Countries and Years
 
-To discovery that country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
+To discover the country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
 
-First, group data;
+First, we grouped and manipulated the data and continued with visulation;
 
@@
 
-Continue with visulation;
-
-```{r}
+```{r, fig.align="center"}
 ####Net Value By Country###
@@
 
-As seen in the graph, only UK gives trade surplus for all years analysed and China, Russia, Germany and USA have the most significant effect on trade deficit.
+As seen in the graph, only UK gives trade surplus for all years analysed. On the other hand China, Russia, Germany and USA have the most significant effect on trade deficit.
 
@@
 The effects of countries are changing year by year.
-So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
+So that, as an alternative perspective we decided to take average net value for all countries in five years and normalized that value to show which country's effects are more than others.
 
-```{r }
+```{r , fig.align="center"}
 #Normalized of Average Values for five years
@@
 
-Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)
+Please follow the link for interactive graph: __[Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)__
 
@@
 
-#### IMAGE EKLENECEK
+#### PIE GRAFIGI DEGISTIRECEGIZ DİYE SHINY DEN IMAGE LARI ALMADIM HENUZ
 
@@
 
-Read the USD and BIST100 index values and rename the columns
+First we read the USD and BIST100 index values and rename the columns; Then proceeded with drawing the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
 
-```{r}
+```{r, fig.align="center"}
 fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
@@
 
-Draw the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
-
-```{r}
+```{r, fig.align="center"}
 sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
@@
 
-Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
+It is concluded that trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
 Besides, there is not a direct correlation between BIST100 index and Trade Deficit Values.
+
+## Conclusion
+
+## References

### 2018-12-19 sourceCode/Analysis_Data_Muh_Clustering.Rmd
Add files via upload

--- 2018-12-16 sourceCode/Analysis_Data_Muh.Rmd
@@
 library(ggplot2)
+library(data.table)
 
@@
 ```
+#K-means Clustering
+```{r}
+country_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Country,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+#country_Adet <-data.table::dcast(country_year, Country ~ year , value.var = c("Adet","Toplam"))
+
+country_Cluster <-dcast(country_year, Country ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+Normalize_country_Cluster<-country_Cluster%>%
+mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
+mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
+mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
+mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
+mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
+select(Country,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)
+
+set.seed(20)
+Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 2, nstart = 20)
+
+head(Cluster)
+
+Normalize_country_Cluster$group<- as.factor(Cluster$cluster)
+
+ggplot(Normalize_country_Cluster, aes(normalized_2016, normalized_2017, color = Normalize_country_Cluster$group)) + geom_point()
+
+```

### 2018-12-19 Draft/Draft20181218.Rmd
.

@@
     toc_float:
-      collapsed: true
+      collapsed: false
       smooth_scroll: false
@@
     code_folding: hide
+    theme: journal
+    #highlight: tango
 
@@
         fontsize.title = 17,type="value",palette = "Set1")
+
 ```
@@
 Please follow the link to access to Shiny app.
-__[Link](https://groupfour.shinyapps.io/tradeOrg)__
+***[Link](https://groupfour.shinyapps.io/tradeOrg)***
 
@@
 
-Please follow the link for interactive graph: __[Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)__
+Please follow the link for interactive graph: ***[Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)***
 

### 2018-12-19 Draft/Draft20181218.Rmd
.

@@
     toc_float:
-      collapsed: false
-      smooth_scroll: false
+      collapsed: true
+      smooth_scroll: true
     number_sections: false

### 2018-12-19 sourceCode/Analysis_Data_Muh_Clustering.Rmd
Update Analysis_Data_Muh_Clustering.Rmd

@@
 set.seed(20)
-Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 2, nstart = 20)
+Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 4, nstart = 20)
 
@@
 ```
+
+```{r}
+product_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Product_Group_Name,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+#country_Adet <-data.table::dcast(country_year, Country ~ year , value.var = c("Adet","Toplam"))
+
+product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+Normalize_product_Cluster<-product_Cluster%>%
+mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
+mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
+mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
+mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
+mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
+select(Product_Group_Name,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)
+
+set.seed(20)
+Cluster <- kmeans(Normalize_product_Cluster[, 2:6], 4, nstart = 20)
+
+head(Cluster)
+
+Normalize_product_Cluster$group<- as.factor(Cluster$cluster)
+
+ggplot(Normalize_product_Cluster, aes(normalized_2013,normalized_2014, color = Normalize_product_Cluster$group)) + geom_point()
+ggplot(Normalize_product_Cluster, aes(normalized_2014,normalized_2015, color = Normalize_product_Cluster$group)) + geom_point()
+ggplot(Normalize_product_Cluster, aes(normalized_2015,normalized_2016, color = Normalize_product_Cluster$group)) + geom_point()
+
+set.seed(20)
+Cluster <- kmeans(product_Cluster[, 2:6], 4, nstart = 20)
+
+head(Cluster)
+
+product_Cluster$group<- as.factor(Cluster$cluster)
+
+ggplot(product_Cluster, aes(Toplam_2013,Toplam_2014, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2014,Toplam_2015, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2015,Toplam_2016, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2016,Toplam_2017, color = product_Cluster$group)) + geom_point()
+
+```

### 2018-12-20 Draft/Draft20181218.Rmd
.

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 # {.tabset .tabset-fade .tabset-pills}
@@
         fontsize.title = 17,type="value",palette = "Set1")
-
 ```
@@
 
+#multiplot(plotCanEx, plotCanIm, plotRusEx, plotRusIm, cols=2)
 #grid.arrange(plotCanEx, plotCanIm,  nrow = 1)

### 2018-12-20 Draft/PresentationDraft.Rmd
.

--- 2018-12-16 Draft.Rmd
@@
 ---
-title: "Group Fou\\*R* Term Project"
-subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
-date: "December 2018"
+title: "Analysis of Turkey's Trade with Selected Countries"
+author: "Group Fou\\*R*"
+date: Dec 26^th^, 2018
 output: 
-  html_document:
-    toc: true
-    toc_float:
-      collapsed: true
-      smooth_scroll: false
-    number_sections: false
-    df_print: paged
-    code_folding: hide
+  ioslides_presentation:
+    widescreen: true
+    smaller: true
+    template: quarterly-report.html
 
+logo: channel4_logo.jpg
 ---
-# Explanatory Data Analysis of Trade Statistics of Turkey {.tabset .tabset-fade .tabset-pills}
 
-## Abstract
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
 
-We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey's trade characteristics by product groups.
-Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017.
-In this study, We applied data manipulation to make it proper for analysis and explanatory data analysis with visulations and conclude with overall statistical overview of Turkey's trade.
-
-## Explanation of Raw Data
-
-Following the extraction from source (Trademap.org), our raw data consist of 10 countries' trade data against Turkey.
-This data splits to 2 with trade direction as 'Export' and 'Import'.
-The other dimension is stat for trade, one is 'Quantity' of Export/Import, the other is 'Value' in thousand USD of Export/Import.
-Therefore we have four main data frame for each country (total of 40 excel files).
-
-<table>
-<thead>
-<tr class="header">
-<th align="left">Data Frame</th>
-<th align="left">DF Definition</th>
-</tr>
-</thead>
-
-<tbody>
-<tr class="odd">
-<td align="left">ExportValues</td>
-<td align="left">Export from Turkey to target countries and their values in thousand USD</td>
-</tr>
-<tr class="odd">
-<td align="left">ExportQuantity</td>
-<td align="left">Export from Turkey to target countries and their quantities in units(tons,gallons etc)</td>
-</tr>
-<tr class="odd">
-<td align="left">ImportValues</td>
-<td align="left">Import to Turkey from target counties and their values in thousand USD</td>
-</tr>
-<tr class="odd">
-<td align="left">ImportQuantity</td>
-<td align="left">Import to Turkey from target counties and their quantities in units(tons,gallons etc)</td>
-</tr>
-
-</tbody>
-</table>
-
-Table structures for "Quantity" and "Value" files are as follows:
-
-<table>
-<thead>
-<tr class="header">
-<th align="left">Country</th>
-<th align="left">Product code</th>
-<th align="left">Product label</th>
-<th align="left">Quantity in 2013</th>
-<th align="left">Unit</th>
-<th align="left">Quantity in 2014</th>
-<th align="left">Unit</th>
-<th align="left">Quantity in 2015</th>
-<th align="left">Unit</th>
-<th align="left">Quantity in 2016</th>
-<th align="left">Unit</th>
-<th align="left">Quantity in 2017</th>
-<th align="left">Unit</th>
-</tr>
-</thead>
-
-<tbody>
-<tr class="odd">
-<td align="left">France</td>
-<td align="left">'0306</td>
-<td align="left">Crustaceans, whether in shell or not, live, fresh, chilled, frozen, dried, salted or in brine, ...</td>
-<td align="left">121</td>
-<td align="left">Tons</td>
-<td align="left">139</td>
-<td align="left">Tons</td>
-<td align="left">22</td>
-<td align="left">Tons</td>
-<td align="left">24</td>
-<td align="left">Tons</td>
-
-</tr>
-</tbody>
-</table>
-
-Table 1: Quantity excel table structure
-
-<table>
-<thead>
-<tr class="header">
-<th align="left">Country</th>
-<th align="left">Product code</th>
-<th align="left">Product label</th>
-<th align="left">Value in 2013</th>
-<th align="left">Value in 2014</th>
-<th align="left">Value in 2015</th>
-<th align="left">Value in 2016</th>
-<th align="left">Value in 2017</th>
-</tr>
-</thead>
-
-<tbody>
-<tr class="odd">
-<td align="left">France</td>
-<td align="left">'0306</td>
-<td align="left">Crustaceans, whether in shell or not, live, fresh, chilled, frozen, dried, salted or in brine, ...</td>
-<td align="left">0</td>
-<td align="left">1155</td>
-<td align="left">1182</td>
-<td align="left">270</td>
-<td align="left">0</td>
-</tr>
-</tbody>
-</table>
-
-Table 2: Values excel table structure
-
-In addition to main raw data, we also have look-up table for product codes; This lookup table registers product labels in 2 digit code that is less categorized than main data.
-
-<table>
-<thead>
-<tr class="header">
-<th align="left">Product code</th>
-<th align="left">Product label</th>
-</tr>
-</thead>
-
-<tbody>
-<tr class="odd">
-<td align="left">'01</td>
-<td align="left">Live animals</td>
-</tr>
-<tr class="odd">
-<td align="left">'02</td>
-<td align="left">Meat and edible meat offal</td>
-</tr>
-<tr class="odd">
-<td align="left">'03</td>
-<td align="left">Fish and crustaceans, molluscs and other aquatic invertebrates</td>
-</tr>
-<tr class="odd">
-<td align="left">'04</td>
-<td align="left">Dairy produce; birds' eggs; natural honey; edible products of animal origin, not elsewhere ...</td>
-</tr>
-
-</tbody>
-</table>
-
-Table 3: Product look-up excel table
-
-Regarding the variables included in these tables; definitions are as follows:
-
-<table>
-<thead>
-<tr class="header">
-<th align="center" colspan="2">ExportQuantity & ImportQuantity</th>
-</tr>
-</thead>
-<tbody>
-<tr class="odd">
-<td align="left">Country</td>
-<td align="left">Trade Partner of Turkey</td>
-</tr>
-<tr class="odd">
-<td align="left">Product_Code</td>
-<td align="left">Traded Product Code in 4 digit</td>
-</tr>
-<tr class="odd">
-<td align="left">Product_Label</td>
-<td align="left">Product Definition</td>
-</tr>  
-<tr class="odd">
-<td align="left">Unit</td>
-<td align="left">Metric of Quantity</td>
-</tr>
-<tr class="odd">
-<td align="left">Quantity_2013</td>
-<td align="left">Export or Import quantity in 2013</td>
-</tr>
-<tr class="odd">
-<td align="left">Quantity_2014</td>
-<td align="left">Export or Import quantity in 2014</td>
-</tr>
-<tr class="odd">
-<td align="left">Quantity_2015</td>
-<td align="left">Export or Import quantity in 2015</td>
-</tr>
-<tr class="odd">
-<td align="left">Quantity_2016</td>
-<td align="left">Export or Import quantity in 2016</td>
-</tr>
-<tr class="odd">
-<td align="left">Quantity_2017</td>
-<td align="left">Export or Import quantity in 2017</td>
-</tr>  
-</tbody>
-</table>
-
-<table>
-<thead>
-<tr class="header">
-<th align="center" colspan="2">ExportValues & ImportValues</th>
-</tr>
-</thead>
-<tbody>
-<tr class="odd">
-<td align="left">Country</td>
-<td align="left">Trade Partner of Turkey</td>
-</tr>
-<tr class="odd">
-<td align="left">Product_Code</td>
-<td align="left">Traded Product Code in 4 digit</td>
-</tr>
-<tr class="odd">
-<td align="left">Product_Label</td>
-<td align="left">Product Definition</td>
-</tr>  
-<tr class="odd">
-<td align="left">Value_2013</td>
-<td align="left">Export or Import value in 2013</td>
-</tr>
-<tr class="odd">
-<td align="left">Value_2014</td>
-<td align="left">Export or Import value in 2014</td>
-</tr>
-<tr class="odd">
-<td align="left">Value_2015</td>
-<td align="left">Export or Import value in 2015</td>
-</tr>
-<tr class="odd">
-<td align="left">Value_2016</td>
-<td align="left">Export or Import value in 2016</td>
-</tr>
-<tr class="odd">
-<td align="left">Value_2017</td>
-<td align="left">Export or Import value in 2017</td>
-</tr>
-</tbody>
-</table>
-
-## Data Preparation, Cleaning and Manipulation
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
+```{r, include=FALSE, message=FALSE, warning=FALSE}
 library(shiny)
@@
 library(plotrix)
+library(treemap)
 ```
 
-In order to read these excel files, firstly we create a function named "getDataSet":
+## Explanation of Raw Data
 
-```{r, warning=FALSE}
+- 10 countries’ trade data against Turkey from [Trademap.org](https://trademap.org/Index.aspx) as 4 seperate excel tables, Export&Import Quantity and Export&Import Values
 
+```{r, include=FALSE}
 PATH <-"C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/Raw Data"
@@
 
-And by using the getDataSet function, we merged the Turkey's export-quantity, export-value, import-quantity, import-value tables for 10 selected countries.
+```{r}
+glimpse(export_quantity_dataset)
+
+```
+
+## Explanation of Raw Data
 
 ```{r}
-glimpse(export_quantity_dataset)
+
 glimpse(export_value_dataset)
-glimpse(import_quantity_dataset)
-glimpse(import_value_dataset)
 ```
 
-We have 13 and 8 variables in quantity and value tables respectively both for export and import.
+## Data Preparation | Joining Quantity, Value Data, Product Labels with 2 Digit Product Codes
 
-Now, it is time to join quantity and value data for both export and import files. While joining the tables, we should also clear the repetitive variable "Unit" for each year.
-
-Also, we need to join product labels in 2 digit product codes to 4 digit product codes and labels.
-
-```{r, warning=FALSE}
+```{r, include=FALSE}
 #read the ProductCodes excel
@@
 export_jTable <- left_join(export_jTable,prdCode,by =c("PcodeTwo"="X__1") )
-
 ```
 
-Now we have joined tables for import and export stats of Turkey.
-
 ```{r}
-glimpse(import_jTable)
 glimpse(export_jTable)
@@
 
-Both tables now have 16 variables and 12,223 rows.
+## Data Preparation | Collating Same Type of Variables
 
-But there is a row in Product_Code column as "TOTAL", we must clear it.
-
-```{r}
+```{r, include=FALSE}
 export_jTable <- export_jTable %>% filter(!grepl("TOTAL", Product_Code))
 import_jTable <- import_jTable %>% filter(!grepl("TOTAL", Product_Code))
-```
 
-We have 16 variables in these tables however quantity and value variables repeat for each year.
-So actually, it is better to organize the table that it will have variables "Year", "Quantity", "Value" instead of 10 columns.
-
-```{r}
 #create new objects for each years' quantity
@@
 
-Now, we have more useful tables, with 9 variables and 61100 rows.
-
 ```{r}
 glimpse(export_jTableMELTED)
-glimpse(import_jTableMELTED)
 ```
 
-## Analysis
+## Analysis | Breakdown of Total Export and Import of Turkey Over Countries
 
-### Breakdown of Total Export and Import of Turkey Over Countries
-
-```{r}
-ttable1=export_jTableMELTED%>%group_by(Country)%>%
-  summarise(co_total=sum(Values,na.rm = TRUE))%>%
-  arrange(desc(co_total,year))
-
+```{r, include=FALSE}
 exptable1=export_jTableMELTED%>%group_by(Country)%>%
@@
 
-pex1_table<-ttable1%>%
-  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+pex1_table<-exptable1%>%
+  mutate(perc_count=(co_total/sum(exptable1$co_total))*100)%>%
   select(Country,co_total,perc_count)
+
+# TREEMAP FOR IMPORT
 
@@
 pim1_table<-imptable1%>%
-  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
+  mutate(perc_count=(co_total/sum(imptable1$co_total))*100)%>%
   select(Country,co_total,perc_count)
-
-lbls_i <- paste(pim1_table$Country,round(pim1_table$perc_count,1)) # add percents to labels
-lbls_i <- paste(lbls_i,"%",sep="") # ad % to labels
-
-pie3D(pim1_table$perc_count,labels=lbls_i,main = "Total Percentage Import Per Countries", explode=0.1, radius=.9,
-      labelcex = 1.2, start=0.7)
-
-lbls_e <- paste(pex1_table$Country,round(pex1_table$perc_count,1)) # add percents to labels
-lbls_e <- paste(lbls_e,"%",sep="") # ad % to labels
-
-pie3D(pex1_table$perc_count,labels=lbls_e,main = "Total Percentage Export Per Countries", explode=0.1, radius=.9,
-             labelcex = 1.2, start=0.7)
 
@@
 
-At import side, Turkeys' biggest trade partners are China, Germany, Russia and US while they are Germany, UK, Italy and USA at export side.
-Germany and USA are the 2 countries exist for both type of trade.
+<div class="columns-2">
 
-When we breakdown this info to years:
+```{r, fig.height=5, fig.width=4.5}
+treemap(pex1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Export Percentage on Countries",
+        fontsize.title = 17,type="value",palette = "Set1")
+```
 
-```{r}
+```{r, fig.height=5, fig.width=4.5}
+treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
+        fontsize.title = 17,type="value",palette = "Set1")
+```
+
+</div>
+
+## Analysis | Breakdown of Total Export and Import of Turkey Over Countries
+
+```{r, fig.align='center'}
 # Export Values in $ 
@@
   geom_bar(stat="identity", position=position_dodge(), colour="black")+
-  ggtitle("Total Import Values in $ to Selected Countries")
+  ggtitle("Import Values")
 
 b<-ggplot(data=ttable, aes(x=Country, y=co_total,fill=year)) +
-  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Total Export Values in $ to Selected Countries")
+  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Export Values")
 
@@
 
-Except Russia, fluctuates over years are not seem so significant.
+## Analysis | Year over Year Changes in Trade Values
 
-In order to deeply understand the data; we build up shiny app with Country, Product and Year variables to review export and import values.
-
-Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrg)
-
-#### YORUM VE IMAGE EKLENECEK
-
-### Analysis of Year by Year Change in Trade Values
-
-```{r}
+```{r, message=FALSE, fig.align='center'}
 tableExport <- export_jTableMELTED %>% 
@@
   filter(year!=2013)
-```
 
-```{r, }
 ggplot(table, aes(x=year)) +
@@
   facet_grid(~variable) +
-   labs(title="YoY Total Value Change",
+   labs(
     x="Year",
@@
 
-```{r}
+## Analysis | Year over Year Changes in Trade Values - Exports to Canada
 
+```{r, fig.align='center', fig.height=5, fig.width=10}
 # Canada and Russia significantly deviates. Investigate these countries in detail with traded products
@@
 
-plotCanEx <- ggplot(summarytableCanadaEx, aes(x=substr(X__2, start = 1, stop = 30))) +
+ggplot(summarytableCanadaEx, aes(x=substr(X__2, start = 1, stop = 30))) +
   geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
@@
   facet_grid(rows = vars(year)) +
-  labs(title="YoY Total Value Change with Canada - Export",
+  labs(
        x="Product Group",
@@
 
-```{r, echo=FALSE}
+## Analysis | Year over Year Changes in Trade Values - Imports From Canada
+
+```{r, fig.align='center', fig.height=5, fig.width=10}
 # Import Analysis
@@
 
-plotCanIm <- ggplot(summarytableCanadaIm, aes(x=substr(X__2, start = 1, stop = 30))) +
+ggplot(summarytableCanadaIm, aes(x=substr(X__2, start = 1, stop = 30))) +
   geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
@@
   facet_grid(rows = vars(year)) +
-  labs(title="YoY Total Value Change Canada - Import",
+  labs(
        x="Product Group",
@@
 
-```{r, echo=FALSE}
+## Analysis | Year over Year Changes in Trade Values - Exports to Russia
 
-# Second Russia
-
-# Export Analysis
-
+```{r, fig.align='center', fig.height=5, fig.width=10}
 summarytableRussianEx <- export_jTableMELTED %>%
@@
 
-plotRusEx <- ggplot(summarytableRussianEx, aes(x=substr(X__2, start = 1, stop = 30))) +
+ggplot(summarytableRussianEx, aes(x=substr(X__2, start = 1, stop = 30))) +
   geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
@@
   facet_grid(rows = vars(year)) +
-  labs(title="YoY Total Value Change Russia - Export",
+  labs(
        x="Product Group",
@@
        Color=c("Year"))
+```
 
-# Import Analysis
+## Analysis | Year over Year Changes in Trade Values - Imports From Russia
 
+```{r, fig.align='center', fig.height=5, fig.width=10}
 summarytableRussianIm <- import_jTableMELTED %>%
@@
 
-plotRusIm <- ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 30))) +
+ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 30))) +
   geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
@@
   facet_grid(rows = vars(year)) +
-  labs(title="YoY Total Value Change Russia - Import",
+  labs(
        x="Product Group",
@@
 
-```{r, echo=FALSE, fig.height=7, fig.width=10 }
-
-plotCanEx
-plotCanIm
-plotRusEx
-plotRusIm
-
-#grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
-#grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
-#fig.height=8, fig.width=16
-```
-
-### Analysis of Trade Deficit by Countries and Years
-
-To discovery that country's effects to trade deficit, we calculated net_value which formulated as 'Export_value - Import_value'. And visualized that value on the basis of year.
-
-First, group data;
-
-```{r }
-export_Product_Group <- export_jTableMELTED%>%
-group_by(Country,PcodeTwo,X__2,year)%>%
-summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
-rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
-
-import_Product_Group <- import_jTableMELTED%>%
-group_by(Country,PcodeTwo,X__2,year)%>%
-summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
-rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
-
-Export_Import_JTable <- export_Product_Group %>%
-  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
-mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
-        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
-select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
-```
-
-Continue with visulation;
-
-```{r}
-####Net Value By Country###
-Net_Value_By_Country <- Export_Import_JTable %>%
-group_by(Country,year)%>%
-summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
-           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))
-
-# Total Net Value fiiled with Country on the basis of Year #
-ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
-  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
-  labs(subtitle="Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
-  coord_flip()+
-  theme(legend.position = "top")
-```
-
-As seen in the graph, only UK gives trade surplus for all years analysed and China, Russia, Germany and USA have the most significant effect on trade deficit.
-
-#### An Alternative perspective to explore effects of countries
-
-The effects of countries are changing year by year.
-So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
-
-```{r }
-#Normalized of Average Values for five years
-Normalized_Values_By_Country <- Export_Import_JTable %>%
-  #filter (year == 2017)%>%
-  group_by(Country)%>%
-  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
-  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
-  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
-
-#Diverging Bars for normalized_Export_value
-ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
-  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
-  scale_fill_manual(name="Normalised Value", 
-                    labels = c("Above Average", "Below Average"), 
-                    values = c("above"="seagreen1", "below"="Red")) +  
-  labs(subtitle="Normalised Net Value for 5 years by Country'", 
-       title= "Diverging Bars") + 
-  coord_flip()
-```
-
-Considering the 5 years period, it is clear that China, Germany and Russia has contribution to trade deficit above average.
-
-We drilled down the analysis for the countries which decreases the average, namely China, Russia and Germany.
-For this aim, we build up shiny app to review the products by defining the Country and ratio showing cumulative percentage of share of products over total import value of this country.
-
-Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)
-
-Through the shiny app, it is understood that
-
-* 70% of import value from China is coming from 8 products 
-* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
-* %70 is from commodities and mineral fuels for import from Russia
-* Only commodities constitute 43% of total import of Russia
-* Vehicles other than railway is the top product imported from Germany
-* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
-
-#### IMAGE EKLENECEK
-
-### Correlation of Trade Deficit with FX Rate and BIST100 index
-
-In order to understand the correlation between trade deficit/surplus and BIST100 index and USD/TL rates, we added this economic indicators to our analysis:
-
-Read the USD and BIST100 index values and rename the columns
-
-```{r}
-fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
-usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)
-
-colnames(usdR) <- c("DateR","ExchangeRate")
-usd <- na.omit(usdR)
-remove(usdR)
-
-usdN<-usd %>% mutate(Date=dmy(DateR))
-usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
-
-fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
-bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)
-
-colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
-bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
-  group_by(Year) %>% 
-  summarise(Value = mean(Value)*1000)
-```
-
-Draw the graph to represent USD/TL rate, BIST100 index and Trade Deficit in time series.
-
-```{r}
-sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
-sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
-joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
-  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
-         Value_2017=Value_2017.y-Value_2017.x) %>%
-  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)
-
-joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
-deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
-                                                                       variable == "Value_2014" ~ 2014,
-                                                                       variable == "Value_2015" ~ 2015,
-                                                                       variable == "Value_2016" ~ 2016,
-                                                                       variable == "Value_2017" ~ 2017)) %>%
-  select(Country,year,value)
-
-deficitPerYear <- deficitPerCountry %>%
-  group_by(year) %>% summarise(value=sum(value))
-
-p<-ggplot() + 
-  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
-  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
-  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
-  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))
-
-print(p)
-
-```
-
-Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 as expected and for the year 2017 we saw the effect of stagflation - while the USD/TL rate increasing (accordingly we know that inflation rate is strongly positively correlatied with the inflation rate (inf rate: 2015-12:5.71%, 2016-12:9.94%, 2017-12:15.47%)) and weak or negative economic growth.
-Besides, there is not a direct correlation between BIST100 index and Trade Deficit Values.
+Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrg)***

### 2018-12-20 Draft/PresentationDraft.Rmd
.

@@
 
-```{r, fig.align='center', fig.height=5, fig.width=10}
+```{r, fig.align='center', fig.height=4.5, fig.width=10}
 summarytableRussianIm <- import_jTableMELTED %>%
@@
 ```
+<div class="centered" class="red2">
+Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrg)***
+</div>
 
-Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrg)***
+## Analysis of Trade Deficit by Countries and Years
+
+```{r, fig.align='center'}
+export_Product_Group <- export_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)
+
+import_Product_Group <- import_jTableMELTED%>%
+group_by(Country,PcodeTwo,X__2,year)%>%
+summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
+rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)
+
+Export_Import_JTable <- export_Product_Group %>%
+  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
+mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
+        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
+select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)
+
+####Net Value By Country###
+Net_Value_By_Country <- Export_Import_JTable %>%
+group_by(Country,year)%>%
+summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
+           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))
+
+# Total Net Value fiiled with Country on the basis of Year #
+ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
+  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
+  labs(title= "Total Net Values") + 
+  coord_flip()+
+  theme(legend.position = "top")
+```

### 2018-12-21 sourceCode/ProjeBusra_2.R
Delete ProjeBusra_2.R

@@ -1,117 +1,0 @@
-library(shiny)
-library(tidyverse)
-library(dplyr)
-library(readxl)
-library(leaflet)
-library(reshape2)
-
-
-githubURL_export <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTable.rds?raw=true")
-githubURL_import <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTable.rds?raw=true")
-githubURL_exportMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTableMELTED.rds?raw=true")
-githubURL_importMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTableMELTED.rds?raw=true")
-
-export_jTable<- readRDS(url(githubURL_export))
-import_jTable<- readRDS(url(githubURL_import))
-export_jTableMELTED<- readRDS(url(githubURL_exportMELTED))
-import_jTableMELTED<- readRDS(url(githubURL_importMELTED))
-
-rm(githubURL_export)
-rm(githubURL_import)
-rm(githubURL_exportMELTED)
-rm(githubURL_importMELTED)
-print("=========")
-
-
-
-unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
-  mutate(Unit_Price = Values/Quantity)
-unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
-  mutate(Unit_Price = Values/Quantity)
-
-unit_price_import <- unit_price_import %>% mutate(type="Import") 
-unit_price_export <- unit_price_export %>% mutate(type="Export")
-
-joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
-  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
-  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
-melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable)
-
-Country <- 
[…]

### 2018-12-21 sourceCode/ProjeBusra_2.R
Add files via upload

@@ -1,0 +1,147 @@
+library(shiny)
+library(tidyverse)
+library(dplyr)
+library(readxl)
+library(leaflet)
+library(reshape2)
+
+
+githubURL_export <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTable.rds?raw=true")
+githubURL_import <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTable.rds?raw=true")
+githubURL_exportMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTableMELTED.rds?raw=true")
+githubURL_importMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTableMELTED.rds?raw=true")
+
+export_jTable<- readRDS(url(githubURL_export))
+import_jTable<- readRDS(url(githubURL_import))
+export_jTableMELTED<- readRDS(url(githubURL_exportMELTED))
+import_jTableMELTED<- readRDS(url(githubURL_importMELTED))
+
+rm(githubURL_export)
+rm(githubURL_import)
+rm(githubURL_exportMELTED)
+rm(githubURL_importMELTED)
+print("=========")
+
+
+
+unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+
+unit_price_import <- unit_price_import %>% mutate(type="Import") 
+unit_price_export <- unit_price_export %>% mutate(type="Export")
+
+joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
+  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
+  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
+melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable) %>% 
[…]

### 2018-12-22 shiny/appbusraShiny.R
son version

@@ -1,0 +1,175 @@
+library(shiny)
+library(tidyverse)
+library(dplyr)
+library(readxl)
+library(DT)
+library(reshape2)
+
+
+githubURL_export <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTable.rds?raw=true")
+githubURL_import <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTable.rds?raw=true")
+githubURL_exportMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/export_jTableMELTED.rds?raw=true")
+githubURL_importMELTED <- ("https://github.com/MEF-BDA503/gpj18-group_four/blob/master/import_jTableMELTED.rds?raw=true")
+
+export_jTable<- readRDS(url(githubURL_export))
+import_jTable<- readRDS(url(githubURL_import))
+export_jTableMELTED<- readRDS(url(githubURL_exportMELTED))
+import_jTableMELTED<- readRDS(url(githubURL_importMELTED))
+
+rm(githubURL_export)
+rm(githubURL_import)
+rm(githubURL_exportMELTED)
+rm(githubURL_importMELTED)
+print("=========")
+
+
+
+unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+
+unit_price_import <- unit_price_import %>% mutate(type="Import") 
+unit_price_export <- unit_price_export %>% mutate(type="Export")
+
+joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
+  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
+  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)%>%
+  filter(Ratio>0 &  !is.nan(Ratio) & Ratio != Inf)
+
[…]

### 2018-12-22 shiny/appbusraShiny.R
busra shny

@@ -75,7 +75,7 @@ ui <- fluidPage(
                   max = 50,
                   step = 0.25,
                   value = 1),
-      selectInput(inputId ="year",label = "Year:",choices = c(2013, 2014, 2015, 2016, 2017)),
+      selectInput(inputId ="year",label = "Year:",choices = c("All",2013, 2014, 2015, 2016, 2017)),
       selectInput(inputId = "Country", label = "Countries:",choices = c(Country)),
       sliderInput("RatioP",
                   "Ratio (Import Unit Price/Export Unit Price)<1",
@@ -107,12 +107,14 @@ server <- function(input, output,session) {
   
   output$distPlot <- renderPlot({
     modified_data <- melted_data
-    #if(input$Country[1] != "" ){
+    
     modified_data <- modified_data%>% filter(Country ==input$Country)
     
-    #}
+    if(input$year != "All" ){
+      modified_data <- modified_data %>% filter(year == input$year )
+      
+    }
     
-    modified_data <- modified_data %>% filter(year==input$year )
     modified_data <- modified_data %>% filter(Ratio>=input$Ratio )
     
     labels1<-substr(modified_data$Product_Label,1,20)
@@ -135,7 +137,11 @@ server <- function(input, output,session) {
     
     #}
     
-    modified_data <- modified_data %>% filter(year==input$year )
+    if(input$year != "All" ){
+      modified_data <- modified_data %>% filter(year == input$year )
+      
+    }
+    
     modified_data <- modified_data %>% filter(Ratio>=input$Ratio )
     
     
@@ -146,7 +152,11 @@ server <- function(input, output,session) {
     modified_data <- melted_data
     
     modified_data <- modified_data%>% filter(Country ==input$Country)
-    modified_data <- modified_data %>% filter(year==input$year )
+    if(input$year != "All" ){
+      modified_data <- modified_data %>% filter(year == input$year )
+      
+    }
+    
     modified_data <- modified_data %>% filter(Ratio>=input$RatioP & Ratio<=1 ) 
     
     labels1<-substr(modified_data$Product_Label,1,20)
@@ -163,7 +173,11 @@ server <- function(input, output,session) {
     modified_data <- joint_table
     
     modified_data <- modified_data%>% filter(Country ==input$Country)
-    modified_data <- modified_data %>% filter(year==input$year )
+    if(input$year != "All" ){
+      modified_data <- modified_data %>% filter(year == input$year )
[…]

### 2018-12-22 Draft/Draft20181218.Rmd

@@
     toc: true
-    toc_float:
-      collapsed: true
-      smooth_scroll: true
+    #toc_float:
+     # collapsed: true
+      #smooth_scroll: true
     number_sections: false
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo=TRUE)
 ```
@@
 
-* 70% of import value from China is coming from 8 products 
-* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
-* %70 is from commodities and mineral fuels for import from Russia
-* Only commodities constitute 43% of total import of Russia
-* Vehicles other than railway is the top product imported from Germany
-* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
+* 70% of import value from China is coming from 8 products while 50% is from electrical machinery, equipments and machinery, mechanical appliances
 
-#### PIE GRAFIGI DEGISTIRECEGIZ DİYE SHINY DEN IMAGE LARI ALMADIM HENUZ
+![Import from China](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\ChinaImport.png)
+
+* Mineral fuels, mineral oils and products of their distillation constitute %21 of import from Russia, while the bigggest product group is classified as "Other""
+
+![Import from Russia](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\RussiaImport.png)
+
+* Vehicles other than railway is the top product imported from Germany and mechanical and electronical machinery and equipments are followed it.
+
+![Import from Germany](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\GermanyImport.png)
 
@@
 
+### Analysis of the Import Unit Prices and Export Unit Prices
+
+In order to understand the products which Turkey is both exporting and importing but importing with more value addition, we calculated unit prices on each product for both import and export and we followed finding the ratio of Import Unit Price / Export Unit Price and groping them in bins of 10.
+
+```{r}
+
+unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+
+unit_price_import <- unit_price_import %>% mutate(type="Import") 
+unit_price_export <- unit_price_export %>% mutate(type="Export")
+
+joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
+  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
+  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
+melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable) %>% 
+  filter(value  >0 & Ratio >0 & Ratio !=Inf ) #& Ratio <=1000 & value <=10000)
+
+melted_data <- melted_data %>% mutate(Bins=0)
+melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
+melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" ) ) %>%  
+  select(Country,Product_Label, year, Ratio, Bins) 
+melted_data <- distinct(melted_data)
+
+ # &  Bins!="21-30"
+```
+
+```{r, fig.align="center", fig.height=7, fig.width=10}
+
+ggplot(melted_data, aes(Bins)) + 
+  geom_bar(aes(fill=year), width = 0.5) +
+
+  facet_wrap(~Country, scales = "free_x") +
+  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 20 times",
+       y="Number of Products",
+       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
+  theme(axis.text.x = element_text(angle=90))
+```
+
+As seen in the graph;
+
+* France, Germany, UK and US are the strongest countries in terms of buying products from Turkey, adding value to these products and selling back to Turkey.
+
+In order to examine the details, we builded ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProUnitP/)*** app.
+
+* xxx
+
+* xxx
+
+* xxx
+
 ## Conclusion
@@
 ## References
+[TradeMap](https://trademap.org/Index.aspx)
+[TCMB](http://tcmb.gov.tr)
+[TUIK](http://www.tuik.gov.tr/)
+[Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
+[R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
+[R-statistics blog](https://www.r-statistics.com/tag/transpose/)

### 2018-12-22 Draft/Draft20181218.Rmd
.

@@
 melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
-melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" ) ) %>%  
+melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" &  Bins!="21-30") ) %>%  
   select(Country,Product_Label, year, Ratio, Bins) 
@@
 
- # &  Bins!="21-30"
+ # 
 ```
@@
   facet_wrap(~Country, scales = "free_x") +
-  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 20 times",
+  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 30 times",
        y="Number of Products",

### 2018-12-22 Draft/Draft20181218.Rmd
.

@@
 
-```{r, fig.align="center"}
+```{r, fig.align="center", fig.height=4, fig.width=6}
 # TREEMAP FOR EXPORT
@@
 
-```{r, fig.align="center"}
+```{r, fig.align="center", fig.height=6, fig.width=8 }
 # Export Values in $ 
@@
   facet_wrap(~Country, scales = "free_x") +
-  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 30 times",
+  labs(title="Number of Products whose ImportUnitPrice/ExportUnitPrice ratio more than 30",
        y="Number of Products",
@@
 
-* France, Germany, UK and US are the strongest countries in terms of buying products from Turkey, adding value to these products and selling back to Turkey.
+* France, Germany, UK and US are the strongest countries in terms of giving strong positive trade balance with variety of product groups while India is the weakest.
 
@@
 
-* xxx
+* Highest ratio products for India is "Yeasts, active or inactive; other dead single-cell micro-organisms" and "Pharmaceutical preparations".
 
-* xxx
+* "Pharmaceutical preparations" is coming in top list for most of the countries.
 
-* xxx
+* USA and UK have 47 and 42 products that have ratio more than 30 and these countries are top 2.
+
+## K-Means Clustering
+
+cvv
 
@@
 
+cvv
+
 ## References
+
 [TradeMap](https://trademap.org/Index.aspx)
+
 [TCMB](http://tcmb.gov.tr)
+
 [TUIK](http://www.tuik.gov.tr/)
+
 [Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
+
 [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
+
 [R-statistics blog](https://www.r-statistics.com/tag/transpose/)

### 2018-12-22 Draft/Draft20181218.Rmd
.

@@
 title: "Explanatory Data Analysis of Trade Statistics of Turkey"
-subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
-date: "December 2018"
 output:
+  pdf_document:
+    toc: yes
   html_document:
     toc: true
-    #toc_float:
-     # collapsed: true
-      #smooth_scroll: true
-    number_sections: false
+    code_folding: hide
     df_print: paged
-    code_folding: hide
+    number_sections: no
     theme: journal
-    #highlight: tango
-
+    toc: yes
+date: "December 2018"
+subtitle: MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group
+  Fou\*R* Term Project
 ---

### 2018-12-22 Draft/Draft20181218.Rmd
Update Draft20181218.Rmd

@@
   html_document:
-    toc: true
     code_folding: hide

### 2018-12-22 Draft/PresentationDraft.Rmd
.

@@
 author: "Group Fou\\*R*"
-date: Dec 26^th^, 2018
+date: "Dec 26^th^, 2018"
 output:
   ioslides_presentation:
-    widescreen: true
-    smaller: true
+    smaller: yes
     template: quarterly-report.html
-
+    widescreen: yes
 logo: channel4_logo.jpg
@@
 ```
+
+## Team Members & Abstract
+
+* [Busra Koc](https://mef-bda503.github.io/pj18-busraakoc/) 
+* [Emre Kemerci](https://mef-bda503.github.io/pj18-EmreKemerci/)
+* [Muharrem Cakir](https://mef-bda503.github.io/pj18-muharremcakir81/)
+* [Omer Bayir](https://mef-bda503.github.io/pj18-omerbayir/)
+* [Salih Ucar](https://mef-bda503.github.io/pj18-ucarsal/)
+
+In this term project, trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) is analysed.
+The aim of the project is to analyze Turkey's export and import characteristics by product groups considering the trade value and quantities.
 
@@
 
-## Analysis of Trade Deficit by Countries and Years
+## Analysis | Trade Deficit by Countries and Years
 
@@
 ```
+
+## Analysis | Countries Effect on Trade Deficit
+
+```{r , fig.align="center"}
+#Normalized of Average Values for five years
+Normalized_Values_By_Country <- Export_Import_JTable %>%
+  #filter (year == 2017)%>%
+  group_by(Country)%>%
+  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
+  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
+  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))
+
+#Diverging Bars for normalized_Export_value
+ggplot(Normalized_Values_By_Country, aes(x=Country, y=normalized_Net_value , label=normalized_Net_value)) + 
+  geom_bar(stat='identity', aes(fill=value_Net_type), width=.5)  +
+  scale_fill_manual(name="Normalised Value", 
+                    labels = c("Above Average", "Below Average"), 
+                    values = c("above"="seagreen1", "below"="Red")) +  
+  labs(subtitle="Normalised Net Value for 5 years by Country'", 
+       title= "Diverging Bars") + 
+  coord_flip()
+```
+<div class="centered" class="red2">
+Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProAnly/)***
+</div>
+
+## Analysis | Correlation of Trade Deficit with FX Rate and BIST100 index
+
+```{r, fig.align="center"}
+fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
+usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)
+
+colnames(usdR) <- c("DateR","ExchangeRate")
+usd <- na.omit(usdR)
+remove(usdR)
+
+usdN<-usd %>% mutate(Date=dmy(DateR))
+usdM<- usdN %>% group_by(year=year(Date)) %>% summarise(Rate=mean(ExchangeRate)*10000000)
+
+fileBIST= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/BIST100.xlsx"
+bist100R <- read_excel(fileBIST, col_names=FALSE, skip=1)
+
+colnames(bist100R) <- c("Date",	"Year","Value",	"Açılış",	"Yüksek",	"Düşük",	"Hac.",	"Fark %")
+bist100 <- bist100R  %>% select(Date,Year,Value) %>% 
+  group_by(Year) %>% 
+  summarise(Value = mean(Value)*1000)
+
+sumImport<- import_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+sumExport<- export_jTable %>% group_by(Country) %>% summarise(Value_2013=sum(Value_2013),Value_2014=sum(Value_2014),Value_2015=sum(Value_2015),Value_2016=sum(Value_2016),Value_2017=sum(Value_2017))
+joinedTableDeficit<-sumExport %>%  inner_join(sumImport,by="Country") %>%
+  mutate(Value_2013=Value_2013.y-Value_2013.x,Value_2014=Value_2014.y-Value_2014.x, Value_2015=Value_2015.y-Value_2015.x, Value_2016=Value_2016.y-Value_2016.x,
+         Value_2017=Value_2017.y-Value_2017.x) %>%
+  select(Country, Value_2013, Value_2014, Value_2015, Value_2016, Value_2017)
+
+joinedTableDeficitMelt <- melt(joinedTableDeficit, id = c("Country"))
+deficitPerCountry<-joinedTableDeficitMelt %>% mutate(year = case_when( variable == "Value_2013" ~ 2013,
+                                                                       variable == "Value_2014" ~ 2014,
+                                                                       variable == "Value_2015" ~ 2015,
+                                                                       variable == "Value_2016" ~ 2016,
+                                                                       variable == "Value_2017" ~ 2017)) %>%
+  select(Country,year,value)
+
+deficitPerYear <- deficitPerCountry %>%
+  group_by(year) %>% summarise(value=sum(value))
+
+ggplot() + 
+  geom_line(data=usdM,aes(x=year, y=Rate,group = 1, colour="USD_TL_Rate"))+
+  geom_line(data=deficitPerYear,aes(x=year, y=value,group = 1, colour="Trade_Deficit"))+
+  geom_line(data=bist100,aes(x=Year, y=Value,group = 1,colour="BIST100_Index")) +
+  scale_colour_manual(name="Indicators",values=c(USD_TL_Rate="red", Trade_Deficit="blue", BIST100_Index="purple"))
+
+```
+
+## Analysis | Analysis of the Import Unit Prices and Export Unit Prices
+
+```{r, fig.align="center", fig.height=4.5, fig.width=10}
+
+unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
+  mutate(Unit_Price = Values/Quantity)
+
+unit_price_import <- unit_price_import %>% mutate(type="Import") 
+unit_price_export <- unit_price_export %>% mutate(type="Export")
+
+joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
+  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
+  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
+melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable) %>% 
+  filter(value  >0 & Ratio >0 & Ratio !=Inf ) #& Ratio <=1000 & value <=10000)
+
+melted_data <- melted_data %>% mutate(Bins=0)
+melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
+melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" &  Bins!="21-30") ) %>%  
+  select(Country,Product_Label, year, Ratio, Bins) 
+melted_data <- distinct(melted_data)
+
+ggplot(melted_data, aes(Bins)) + 
+  geom_bar(aes(fill=year), width = 0.5) +
+
+  facet_wrap(~Country, scales = "free_x") +
+  labs(title="Number of Products whose ImportUnitPrice/ExportUnitPrice ratio more than 30",
+       y="Number of Products",
+       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
+  theme(axis.text.x = element_text(angle=90))
+```
+<div class="centered" class="red2">
+Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProUnitP/)***
+</div>
+
+## Analysis | K-Means Clustering
+
+## Conclusion

### 2018-12-22 Draft/PresentationDraft.Rmd
.

@@
 
+<div class="columns-2">
+
 * [Busra Koc](https://mef-bda503.github.io/pj18-busraakoc/)
@@
 The aim of the project is to analyze Turkey's export and import characteristics by product groups considering the trade value and quantities.
+
+The purpose of the analysis is to understand the Turkey's trade Statistics for two way and with ten important countries.
+
+Describe Turkey's the trade deficit with the country,year and product dimensions. Try to clear which factors effects deficit in trade, and is there relation deficit and other financials.
+
+A clear understanding of the data to see if we can locate useful insights about which products and countries will remain the deficit and wich of them will be strategic for Turkey
+
+</div>
 
@@
 
-```{r}
+```{r, fig.align='center'}
 glimpse(export_quantity_dataset)
@@
 
-```{r}
+```{r, fig.align='center'}
 
@@
 
-```{r}
+```{r, fig.align='center'}
 glimpse(export_jTable)
@@
 
-```{r}
+```{r, fig.align='center'}
 glimpse(export_jTableMELTED)

### 2018-12-22 Draft/Draft20181218.Rmd
Update Draft20181218.Rmd

@@
 library(treemap)
+library(cluster)
+library(factoextra)
 ```
@@
 
-cvv
+```{r}
+product_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Product_Group_Name,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+#country_Adet <-data.table::dcast(country_year, Country ~ year , value.var = c("Adet","Toplam"))
+
+product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+#Normalize_product_Cluster<-product_Cluster%>%
+#mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
+#mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
+#mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
+#mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
+#mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
+#select(Product_Group_Name,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)
+
+#set.seed(20)
+#Cluster <- kmeans(Normalize_product_Cluster[, 2:6], 4, nstart = 20)
+
+#head(Cluster)
+
+#Normalize_product_Cluster$group<- as.factor(Cluster$cluster)
+
+#ggplot(Normalize_product_Cluster, aes(normalized_2013,normalized_2014, color = Normalize_product_Cluster$group)) + geom_point()
+#ggplot(Normalize_product_Cluster, aes(normalized_2014,normalized_2015, color = Normalize_product_Cluster$group)) + geom_point()
+#ggplot(Normalize_product_Cluster, aes(normalized_2015,normalized_2016, color = Normalize_product_Cluster$group)) + geom_point()
+
+distance <- get_dist(product_Cluster)
+fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
+
+k2 <- kmeans(product_Cluster[, 2:6], centers = 2, nstart = 25)
+str(k2)
+
+#fviz_cluster(k2, data = product_Cluster)
+
+set.seed(20)
+Cluster <- kmeans(product_Cluster[, 2:6], 4, nstart = 20)
+
+head(Cluster)
+
+product_Cluster$group<- as.factor(Cluster$cluster)
+
+ggplot(product_Cluster, aes(Toplam_2013,Toplam_2014, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2014,Toplam_2015, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2015,Toplam_2016, color = product_Cluster$group)) + geom_point()
+ggplot(product_Cluster, aes(Toplam_2016,Toplam_2017, color = product_Cluster$group)) + geom_point()
+
+```
 

### 2018-12-23 Draft/Draft20181218.Rmd
.

--- 2018-12-22 Draft/Draft20181218.Rmd
@@
 
-cvv
+```{r}
+product_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Product_Group_Name,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+product_Cluster2 <- product_Cluster[,-1]
+rownames(product_Cluster2) <- substr(product_Cluster$Product_Group_Name, start=1, stop=47)
+
+#Scale the values
+
+product_Cluster2 <- scale(product_Cluster2)
+head(product_Cluster2)
+
+# Create distance matrix
+distance <- get_dist(product_Cluster2)
+fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
+
+#Determine optimal cluster with Elbow Method
+set.seed(11)
+fviz_nbclust(product_Cluster2, kmeans, method = "wss")
+
+#Determine Optimal Cluster with Silhoutte Method
+fviz_nbclust(product_Cluster2, kmeans, method = "silhouette")
+
+#Determine Optimal Cluster with Gap Statistics Method
+set.seed(12)
+gap_stat <- clusGap(product_Cluster2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
+fviz_gap_stat(gap_stat)
+
+# Compute k-means with 4 clusters 
+k2 <- kmeans(product_Cluster2, centers = 4, nstart = 25)
+print (k2)
+fviz_cluster(k2, data = product_Cluster2)
+
+"cluster: A vector of integers (from 1:k) indicating the cluster to which each point is allocated.
+centers: A matrix of cluster centers.
+totss: The total sum of squares.
+withinss: Vector of within-cluster sum of squares, one component per cluster.
+tot.withinss: Total within-cluster sum of squares, i.e. sum(withinss).
+betweenss: The between-cluster sum of squares, i.e. $totss-tot.withinss$.
+size: The number of points in each cluster."
+
+```
 

### 2018-12-23 Final/Final20181223.Rmd
.

--- 2018-12-22 Draft/Draft20181218.Rmd
@@
 output:
-  pdf_document:
-    toc: yes
   html_document:
@@
     theme: journal
+    toc: yes
+  pdf_document:
     toc: yes
@@
 
-## K-Means Clustering
+## K-Means Clustering for Value of Turkey Exports on Products
 
-cvv
+In order to see how products, which is exported to Turkey, cluster, we implemented k-means clustering method after scaling the values
+
+To determine optimal cluster number, we checked Elbow, Silhoutte and Gap Statistics methods and also we draw distance matrix for products according to export values for 5 years.
+
+```{r, fig.align="center"}
+product_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Product_Group_Name,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+product_Cluster2 <- product_Cluster[,-1]
+rownames(product_Cluster2) <- substr(product_Cluster$Product_Group_Name, start=1, stop=47)
+
+#Scale the values
+
+product_Cluster2 <- scale(product_Cluster2)
+
+#head(product_Cluster2)
+
+# Create distance matrix
+distance <- get_dist(product_Cluster2)
+fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
+
+#Determine optimal cluster with Elbow Method
+set.seed(11)
+Elbow <- fviz_nbclust(product_Cluster2, kmeans, method = "wss")
+
+#Determine Optimal Cluster with Silhoutte Method
+Silhoutte <- fviz_nbclust(product_Cluster2, kmeans, method = "silhouette")
+
+#Determine Optimal Cluster with Gap Statistics Method
+set.seed(12)
+gap_stat <- clusGap(product_Cluster2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
+GapStat <- fviz_gap_stat(gap_stat)
+
+grid.arrange(Elbow, Silhoutte, GapStat, nrow = 1)
+
+```
+
+It looks like it is better to cluster the data into 2, 3 or 4. So we computed the k-means with 2, 3 and 4 cluster as seen below.
+
+```{r, fig.align="center"}
+
+# Compute k-means with 2,3 and 4 clusters 
+k1 <- kmeans(product_Cluster2, centers = 2, nstart = 25)
+k2 <- kmeans(product_Cluster2, centers = 3, nstart = 25)
+k3 <- kmeans(product_Cluster2, centers = 4, nstart = 25)
+
+#print (k3)
+
+k1p <- fviz_cluster(k1, data = product_Cluster2, geom = "point") + ggtitle("k = 2")
+k2p <- fviz_cluster(k2, data = product_Cluster2, geom = "point") + ggtitle("k = 3")
+k3p <- fviz_cluster(k3, data = product_Cluster2, geom = "point") + ggtitle("k = 4")
+
+grid.arrange(k1p, k2p, k3p, nrow = 3)
+
+fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")
+
+#cluster: A vector of integers (from 1:k) indicating the cluster to which each point is allocated.
+#centers: A matrix of cluster centers.
+#totss: The total sum of squares.
+#withinss: Vector of within-cluster sum of squares, one component per cluster.
+#tot.withinss: Total within-cluster sum of squares, i.e. sum(withinss).
+#betweenss: The between-cluster sum of squares, i.e. $totss-tot.withinss$.
+#size: The number of points in each cluster."
+
+```
+
+With 4 clusters, it is seen that;
+
+* Vehicles other than railway can be classified as a group - the export products we spent too much money
+
+* Machinery, mechanical appliances, electronical machinery and equipments, clothing is another classification - top2 products in terms of money spent
+
+* Third class consist of iron, steel, pearls, ores etc. and this class slightly differs from 4th group in terms of money spent
 
@@
 
-cvv
+As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;
+
+* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
+* Germany and USA are the 2 top countries seen in both directions of trade.
+* Generally we have fluctuated trade trend with Russia.
+* Turkey's trade deficit analyisis gives the results : 
+  + UK gives trade surplus for all years analysed 
+  + China, Russia, Germany and USA have the most significant effect on trade deficit
+  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
+  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
+      + Electrical machinery, equipments and machinery, mechanical appliances
+      + Mineral fuels, mineral oils and products of their distillation constitute 
+      + Vehicles other than railway and mechanical and electronical machinery and equipments
+* As a result of clustering exported products;
+  + Vehicles other than railway is the group we spent the most money
+  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.
 
@@
 [R-statistics blog](https://www.r-statistics.com/tag/transpose/)
+
+[UC Business Analytics R Programming Guide](https://uc-r.github.io/kmeans_clustering#silo)

### 2018-12-23 Final/PresentationFinal.Rmd
.

--- 2018-12-22 Draft/PresentationDraft.Rmd
@@
 
-## Analysis | K-Means Clustering
+## K-Means Clustering | Determining Optimal Cluster
+
+```{r, fig.align="center"}
+product_year<-export_Product_Group %>%
+filter(Export_Value > 0) %>%
+group_by(Product_Group_Name,year)%>%
+summarise(Adet=n(), Toplam = sum(Export_Value))
+
+product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
+   rename(Toplam_2013 = "2013") %>%
+   rename(Toplam_2014 = "2014") %>%
+   rename(Toplam_2015 = "2015") %>%
+   rename(Toplam_2016 = "2016") %>%
+   rename(Toplam_2017 = "2017")
+
+product_Cluster2 <- product_Cluster[,-1]
+rownames(product_Cluster2) <- substr(product_Cluster$Product_Group_Name, start=1, stop=47)
+
+#Scale the values
+
+product_Cluster2 <- scale(product_Cluster2)
+
+#head(product_Cluster2)
+
+# Create distance matrix
+distance <- get_dist(product_Cluster2)
+#fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
+
+#Determine optimal cluster with Elbow Method
+set.seed(11)
+Elbow <- fviz_nbclust(product_Cluster2, kmeans, method = "wss")
+
+#Determine Optimal Cluster with Silhoutte Method
+Silhoutte <- fviz_nbclust(product_Cluster2, kmeans, method = "silhouette")
+
+#Determine Optimal Cluster with Gap Statistics Method
+set.seed(12)
+gap_stat <- clusGap(product_Cluster2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
+GapStat <- fviz_gap_stat(gap_stat)
+
+grid.arrange(Elbow, Silhoutte, GapStat, nrow = 1)
+
+```
+
+## K-Means Clustering | Computing K-Means
+
+```{r, fig.align="center"}
+
+# Compute k-means with 2,3 and 4 clusters 
+k1 <- kmeans(product_Cluster2, centers = 2, nstart = 25)
+k2 <- kmeans(product_Cluster2, centers = 3, nstart = 25)
+k3 <- kmeans(product_Cluster2, centers = 4, nstart = 25)
+
+#print (k3)
+
+k1p <- fviz_cluster(k1, data = product_Cluster2, geom = "point") + ggtitle("k = 2")
+k2p <- fviz_cluster(k2, data = product_Cluster2, geom = "point") + ggtitle("k = 3")
+k3p <- fviz_cluster(k3, data = product_Cluster2, geom = "point") + ggtitle("k = 4")
+
+grid.arrange(k1p, k2p, k3p, nrow = 3)
+
+```
+
+## K-Means Clustering | Computing K-Means
+
+```{r, fig.align="center"}
+
+fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")
+
+```
 
 ## Conclusion
+
+As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;
+
+* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
+* Germany and USA are the 2 top countries seen in both directions of trade.
+* Generally we have fluctuated trade trend with Russia.
+* Turkey's trade deficit analyisis gives the results : 
+  + UK gives trade surplus for all years analysed 
+  + China, Russia, Germany and USA have the most significant effect on trade deficit
+  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
+  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
+      + Electrical machinery, equipments and machinery, mechanical appliances
+      + Mineral fuels, mineral oils and products of their distillation constitute 
+      + Vehicles other than railway and mechanical and electronical machinery and equipments
+
+## Conclusion
+
+* As a result of clustering exported products;
+  + Vehicles other than railway is the group we spent the most money
+  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.
+
+## Thanks - Q & A
+
+![](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\4logo.png)
+
+For the full report and workpapers, please refer to [Group Fou*R* GitHub Pages](https://mef-bda503.github.io/gpj18-group_four/)

### 2018-12-23 Final/Final20181223.Rmd
.

@@
 
-In order to see how products, which is exported to Turkey, cluster, we implemented k-means clustering method after scaling the values
+In order to see the segmentation of exported products by Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.
 
@@
 
-```{r, fig.align="center"}
+```{r, fig.align="center", fig.height=5 , fig.width=8}
 product_year<-export_Product_Group %>%
@@
 
+```
+
+```{r, fig.align="center", fig.height=4 , fig.width=10}
 #Determine optimal cluster with Elbow Method
@@
 
-```{r, fig.align="center"}
+```{r, fig.align="center", fig.height=7 , fig.width=10}
 
@@
 grid.arrange(k1p, k2p, k3p, nrow = 3)
-
-fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")
 
@@
 
+```
+
+```{r, fig.align="center", fig.height=8 , fig.width=15}
+fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")
 ```
@@
 [UC Business Analytics R Programming Guide](https://uc-r.github.io/kmeans_clustering#silo)
+
+[r-statistics.co](http://r-statistics.co/)

### 2018-12-25 Final/Final20181223.Rmd
.

@@
 
-In order to see the segmentation of exported products by Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.
+In order to see the segmentation of exported products from Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.
 
@@
 
-* Vehicles other than railway can be classified as a group - the export products we spent too much money
-
-* Machinery, mechanical appliances, electronical machinery and equipments, clothing is another classification - top2 products in terms of money spent
-
-* Third class consist of iron, steel, pearls, ores etc. and this class slightly differs from 4th group in terms of money spent
+* Vehicles other than railway can be classified as a group - the export products we earned the most money
+
+* Machinery, mechanical appliances, electronical machinery and equipments, clothing is another classification - top2 products in terms of money earned
+
+* Third class consist of iron, steel, pearls, ores etc. and this class slightly differs from 4th group
 
@@
 * As a result of clustering exported products;
-  + Vehicles other than railway is the group we spent the most money
+  + Vehicles other than railway is the group we earned the most money
   + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.

### 2018-12-25 Final/PresentationFinal.Rmd
.

@@
 logo: channel4_logo.jpg
+
 ---
@@
 
-## Explanation of Raw Data
+## Explanation of Raw Data and Data Preparation
 
-- 10 countries’ trade data against Turkey from [Trademap.org](https://trademap.org/Index.aspx) as 4 seperate excel tables, Export&Import Quantity and Export&Import Values
+- 10 countries’ trade data against Turkey are taken from [Trademap.org](https://trademap.org/Index.aspx) as 4 seperate excel tables, Export&Import Quantity and Export&Import Values
+
+- Quantity and Value tables joined following the binding operation of 10 countries tables. Besides, 2 digit product code table have been joined.
+
+- Same type of variables collated to one and "years"" melted to prevent repetition of quantity and value variables.
 
@@
 
-```{r, fig.align='center'}
+```{r, fig.align='center', include= FALSE}
 glimpse(export_quantity_dataset)
@@
 
-## Explanation of Raw Data
-
-```{r, fig.align='center'}
+```{r, fig.align='center', include=FALSE}
 
@@
 ```
-
-## Data Preparation | Joining Quantity, Value Data, Product Labels with 2 Digit Product Codes
 
@@
 
-```{r, fig.align='center'}
+```{r, fig.align='center', fig.height=5, fig.width=4.5, include=FALSE}
 glimpse(export_jTable)
 ```
-
-## Data Preparation | Collating Same Type of Variables
 
@@
 
-## Analysis | Breakdown of Total Export and Import of Turkey Over Countries
+## Analysis | Breakdown of Total Export & Import
 
-```{r, fig.align='center'}
+<div class="columns-2">
+
+```{r, fig.align='center', fig.height=5, fig.width=5}
 # Export Values in $ 
@@
   geom_bar(stat="identity", position=position_dodge(), colour="black")+
-  ggtitle("Import Values")
+  ggtitle("Import Values") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
 b<-ggplot(data=ttable, aes(x=Country, y=co_total,fill=year)) +
-  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Export Values")
+  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Export Values") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
 
-## Analysis | Year over Year Changes in Trade Values
-
-```{r, message=FALSE, fig.align='center'}
+```{r, message=FALSE, fig.align='center', fig.height=5, fig.width=5}
 tableExport <- export_jTableMELTED %>% 
@@
 
-## Analysis | Year over Year Changes in Trade Values - Exports to Canada
+</div>
 
-```{r, fig.align='center', fig.height=5, fig.width=10}
+## Analysis | Year over Year Changes in Trade Values - Export & Import - Canada {#slide36}
+
+<style> 
+  #slide36 > p { 
+    margin-top: -50px; 
+  } 
+</style>
+
+<div class="columns-2">
+
+```{r, fig.align='center', fig.height=5, fig.width=5}
 # Canada and Russia significantly deviates. Investigate these countries in detail with traded products
@@
 
-## Analysis | Year over Year Changes in Trade Values - Imports From Canada
-
-```{r, fig.align='center', fig.height=5, fig.width=10}
+```{r, fig.align='center', fig.height=5, fig.width=5}
 # Import Analysis
@@
 
-## Analysis | Year over Year Changes in Trade Values - Exports to Russia
+</div>
 
-```{r, fig.align='center', fig.height=5, fig.width=10}
+## Analysis | Year over Year Changes in Trade Values - Exports & Imports to Russia {#slide37}
+
+<style> 
+  #slide37 > p { 
+    margin-top: -50px; 
+  } 
+</style>
+
+<div class="columns-2">
+
+```{r, fig.align='center', fig.height=5, fig.width=5}
 summarytableRussianEx <- export_jTableMELTED %>%
@@
 
-## Analysis | Year over Year Changes in Trade Values - Imports From Russia
-
-```{r, fig.align='center', fig.height=4.5, fig.width=10}
+```{r, fig.align='center', fig.height=4.5, fig.width=5}
 summarytableRussianIm <- import_jTableMELTED %>%
@@
 
-## Analysis | Trade Deficit by Countries and Years
+</div>
 
-```{r, fig.align='center'}
+## Analysis | Trade Deficit and Effects of Countries on Trade Deficit
+
+<div class="columns-2">
+
+```{r, fig.align='center', fig.height=4.5, fig.width=6}
 export_Product_Group <- export_jTableMELTED%>%
@@
 
-## Analysis | Countries Effect on Trade Deficit
-
-```{r , fig.align="center"}
+```{r , fig.align="center", fig.height=4.5, fig.width=6}
 #Normalized of Average Values for five years
@@
 
-## Analysis | Correlation of Trade Deficit with FX Rate and BIST100 index
+</div>
 
-```{r, fig.align="center"}
+```{r, fig.align="center", include=FALSE}
 fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
@@
 
-## K-Means Clustering | Determining Optimal Cluster
-
-```{r, fig.align="center"}
+```{r, fig.align="center", include=FALSE}
 product_year<-export_Product_Group %>%
@@
 
-## K-Means Clustering | Computing K-Means
+## K-Means Clustering
 
-```{r, fig.align="center"}
+<div class="columns-2">
+
+```{r, fig.align="center", fig.height=5.5, fig.width=4}
 
@@
 
-## K-Means Clustering | Computing K-Means
-
-```{r, fig.align="center"}
+```{r, fig.align="center", fig.height=5.5, fig.width=5.5}
 
@@
 
-## Conclusion
+</div>
 
-As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;
+## Conclusion {#slide38}
 
-* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
-* Germany and USA are the 2 top countries seen in both directions of trade.
-* Generally we have fluctuated trade trend with Russia.
-* Turkey's trade deficit analyisis gives the results : 
-  + UK gives trade surplus for all years analysed 
-  + China, Russia, Germany and USA have the most significant effect on trade deficit
-  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
-  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
-      + Electrical machinery, equipments and machinery, mechanical appliances
-      + Mineral fuels, mineral oils and products of their distillation constitute 
-      + Vehicles other than railway and mechanical and electronical machinery and equipments
+<style> 
+  #slide38 > p { 
+    margin-top: -50px; 
+  } 
+</style>
 
-## Conclusion
+<font size="3">As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;</font>
 
-* As a result of clustering exported products;
-  + Vehicles other than railway is the group we spent the most money
-  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.
+* <font size="3">Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side.</font> 
+* <font size="3">Germany and USA are the 2 top countries seen in both directions of trade.</font>
+* <font size="3">Generally we have fluctuated trade trend with Russia.</font>
+* <font size="3">Turkey's trade deficit analyisis gives the results :</font> 
+  + <font size="2">UK gives trade surplus for all years analysed</font> 
+  + <font size="2">China, Russia, Germany and USA have the most significant effect on trade deficit</font>
+  + <font size="2">Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.</font>
+  + <font size="2">Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :</font>
+      + <font size="2">Electrical machinery, equipments and machinery, mechanical appliances</font>
+      + <font size="2">Mineral fuels, mineral oils and products of their distillation constitute</font> 
+      + <font size="2">Vehicles other than railway and mechanical and electronical machinery and equipments</font>
+* <font size="3">As a result of clustering exported products;</font>
+  + <font size="2">Vehicles other than railway is the group we spent the most money</font>
+  + <font size="2">Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.</font>
 

### 2018-12-26 Final/PresentationFinal.Rmd
.

@@
 
-```{r, fig.align='center', fig.height=4.5, fig.width=6}
+```{r, fig.align='center', fig.height=4.5, fig.width=5}
 export_Product_Group <- export_jTableMELTED%>%
